### 2020-04-25 COORDINATION2020/paper.tex
paper6 update

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{verbatim}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{url}
\begin{document}
%
\title{Towards a Formally Verified EVM in Production Environment}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Xiyue Zhang\inst{1} \and
Yi Li\inst{1} \and
Meng Sun\inst{1}
}
%
% \authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{School of Mathematical Sciences, Peking University
\\
\email{\{xiyuezhang, liyi\_math, sunm\}@pku.edu.cn}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Among dozens of decentralized computing platforms, Ethe\-reum attracts widespread attention for its native support of smart contracts by means of a virtual machine called EVM. Programs can be developed in various front-end languages. For example, Solidity can be deployed to the blockchain in the form of compiled EVM opcodes. However, such flexibility leads to critical safety challenges. In this paper, we formally define the behavior of EVM in Why3, a platform for deductive program verification, which facilitates the verification of different properties. Furthermore, the extracted implementation in OCaml can be directly integrated into the production environment and tested against the standard test suite. The combination of proofs and testing in our framework serves as a powerful analysis basis for EVM and smart contracts.

\keywords{EVM \and Why3 \and Verification \and Testing.}
\end{abstract}
%
%
%
\section{Introduction}
Ever since the inception of the Bitcoin \cite{nakamoto2008bitcoin} blockchain system, cryptocurrencies have become a global revolutionary phenomenon known to majority of people. Meanwhile, the decentralized system with no server or central authority, which emerges as a side product of Bitcoin, shows great potential in carrying out secure online transactions. From then until now, there have been so much change and growth on blockchain technology. The researchers and developers see plenty of potential and massive possibilities of blockchain applications, especially in financial, governmental services. Ethereum\cite{Ethereum} extends Bitcoin's design, which can not only process transactions but also process complex smart contracts and programs. This feature makes Ethereum a popular ecosystems for building blockchain-applications, which gains much more interest to innovate the options to utilize blockchain.

Smart contracts are often written in a high level programming language called \textit{Solidity} \cite{solidity} and then compiled into low-level machine instructions (\textit{opcodes}), which is encoded into bytecode. Ethereum Virtual Machine (EVM) is a quasi-Turing complete machine which implements the execution model of the Ethereum. Given a sequence of bytecode instructions, which are compiled from smart contracts by EVM compiler, and the environment data, this execution model specifies how the blockchain transits from one state to another.

However, EVM and smart contracts are faced with several security vulnerabilities. Atzei et al. presented a taxonomy of vulnerabilities and related attacks against Solidity, the EVM, and the blockchain in \cite{atzei2016survey}. The adoption of formal methods can facilitate the production of trustworthy and reliable software systems. Verification such as theorem proving techniques and testing have become essential to guarantee the correctness of safety-critical systems.

To address the security challenges against EVM, we present a framework of generating formally verified EVM for production environment in this paper. The contributions of this work are: Firstly, a formal definition of EVM is specified in WhyML, the language of programming and specification in Why3. Secondly, an implementation of EVM in OCaml is generated through an extraction mechanism based on a series of customized drivers. Lastly, the verification of sample properties and testing of the OCaml implementation for EVM against a standard test suite for Ethereum.

This paper is organized as follows: Section \ref{Sec: Pre} presents some background about Why3, Ethereum Virtual Machine (EVM) and smart contracts. We outline the framework for formalizing, property verifying and testing of EVM in Section \ref{Sec: Framework}. Based on the framework, we perform some experiments in Section \ref{Sec: Experiment} and highlight th e verification and testing results for the properties of EVM. Section \ref{Sec: Related} presents some related work. Finally, we summarized this paper and point out the future research direction in Section \ref{Sec: Conclusion}.

\section{Preliminary}\label{Sec: Pre}
\subsection{Why3}
Why3\cite{filliatre2013why3} is a tool for deductive program verification. It provides a standard library of logical theories, such as integer and real arithmetic, and basic programming data structures, such as arrays and queues. WhyML is the programming and specification language of Why3. The specification language is used to write program annotations and background logical theories, which serves as a common format for proof goals. Ghost code is also supported in WhyML, which serves to facilitate verification without affecting the final result of a program.

With the specification language formalizing the properties, a verification condition (VC) generator can produce the proof obligations that need to be discharged. Furthermore, logical goals can be proved using a series of automated or interactive theorem provers, including Alt-Ergo, CVC3, CVC4, Z3, Coq and PVS. To get the executable code, users can write programs in WhyML and obtain correct-by-construction OCaml programs through an automated extraction mechanism. In the extraction process, uninterpreted WhyML types are either mapped to existing OCaml type or left as abstract data type. And such mapping can be customized through user-defined drivers. 
\subsection{EVM and Smart Contract}
Different from the general virtual machine, Ethereum Virtual Machine (EVM) is designed to serve as a run-time environment for smart contracts, whose specification is tersely defined in Ethereum Yellow Paper\cite{wood2014ethereum}.
EVM is a 256-bit register stack-based architecture, which can store 1024 items at most. The memory model of EVM is a volatile word-addressed byte array. Some opcodes use contract memory to retrieve or pass data. When some contract execution finishes, the memory contents are cleared. Unlike the memory model, the storage model of EVM is non-volatile which acts like a database. The data stored in \textit{storage} is accessible for future contract executions.

Smart contracts are essentially programs deployed on the Ethereum blockchain used to conduct transactions or perform specific actions. Any user can create a contract by posting a transaction to the blockchain. The program code of the contract is fixed after deployment and it will be invoked whenever it receives a transaction. 
\section{EVM Framework}\label{Sec: Framework}
\subsection{Methodology of EVM Framework}
This framework can be considered as an experiment in a methodology that combines verification and testing for developing secure EVM implementations, and also as a tool for verifying smart contracts after compiling into bytecodes. Figure TOREF outlines the whole framework for developing a formally verified EVM in production environment.
\subsection{EVM in Why3}
According to the Ethereum project yellow paper\cite{wood2014ethereum}, we translated EVM into Why3, which provides a programming and specification language WhyML. Based on the EVM definitions, Why3 further generates verification conditions according to the property specification, and allows the users to split the goals into different subgoals and prove each subgoal through different Satisfiability Modulo Theories (SMT) solvers. In cases when the automatic SMT slovers cannot deal with, users can resort to interactive theorem proves based on the files generated by Why3.

As have been mentioned before, EVM is a simple stack-based machine. The memory model of EVM is a word-addressed byte array, which is volatile. The storage model of EVM is a non-volatile word-addressed word array. The perspective we see the execution process of a sequence of opcodes (instructions), which could be complied from a smart contract, is as a state transition process and it finally leads to a series of changes in the stack, memory and etc.

\subsubsection{Type Definition}
Based on the needs of type requirements of Ethereum, such as that the machine word of EVM is 256 bits and the address is 160 bits, we developed a series of type modules \texttt{UInt256}, \texttt{UInt160} and etc. to ease the representation of the corresponding types in Ethereum. Why3 also supports type alias which makes the source code in WhyML more readable. 
Stack is defined as a list of elements whose type are \texttt{uint256}, aliased by \texttt{machword}. Memory is defined as a function that maps \texttt{machword} to an option type \texttt{option memory\_content}. The \texttt{memory\_content} is an enumeration type including \texttt{Item8} and \texttt{Item256} since the memory content could be accessed through 256-bit store and 8-bit store instructions. Storage is defined as a function that maps \texttt{machword} to \texttt{machword}. There are also other enumeration types defined to reflect the virtual machine status, the operation error, and a big view of the returned result which are \texttt{vmstatus}, \texttt{error} and \texttt{return\_type}. The record type \textt{machine\_state} represents the machine state whose components contain stack, memory, program counter, vmstatus, the instruction list and etc..

\subsubsection{Instruction Definition}
Inspired by the instruction formalization of EVM in Lem \cite{hirai2017defining}, we defined the instruction set in different groups, such as arithmetic operations, stack operations and etc., then integrated them into a final type definition. The final instruction type definition is presented as follows, which shows the different instruction groups:
\begin{verbatim}
type instruction =
  | Invalid byte
  | Arith arith_inst  
  | Sarith sign_arith_inst
  | Bits bits_inst
  | Info info_inst
  | Memory memory_inst
  | Storage storage_inst
  | Pc pc_inst
  | Stack stack_inst
  | Dup dup_inst
  | Swap swap_inst
  | Log log_inst
  | System system_inst
\end{verbatim}
The organization of the instruction group is a bit different from the yellow paper\cite{wood2014ethereum}. The comparison operations are contained in the arithmetic operations \texttt{Arith} and the comparison operations for signed arithmetic are contained in the signed arithmetic operations \texttt{Sarith}, respectively. The bitwise operations and \texttt{BYTE} operation are included in the bit-related instructions \texttt{Bits}. Almost all of the information related instructions including environmental and block information are defined in type \texttt{info\_inst}, except some \texttt{CALL} and \texttt{CODE} instructions like the \texttt{CALLDATACOPY}, \texttt{CODECOPY} and \texttt{CALLDATALOAD} which are closely related to memory and stack. Therefore, for the memory and stack instruction groups, some extra instructions are added to the original instruction subsets presented in the yellow paper. In case when there exists some instruction that is illegal, the instruction \texttt{Invalid} is included in the instruction type definition. The \texttt{STOP} operation and the system operations from the yellow paper except \texttt{Invalid} are contained in the \textit{System} instruction set. As for the remaining instruction groups, they are basically the same as the corresponding instruction subsets in \cite{wood2014ethereum}. 
\subsubsection{Interpreter Definition}
The function interpreter maps from some machine state to a new machine state, mainly in charge of formalizing the state transition result of different instructions.
In order to make the definition of interpreter more concise, we defined some auxiliary functions. For example, the following function is used to obtain the instruction which needs to be executed from the instruction list according to the program counter. 
\begin{verbatim}
let get_inst (mac_st: machine_state): option instruction =
  match mac_st.mac_pc, mac_st.mac_insts with 
  | pc, insts -> (nth pc insts) 
  end    
\end{verbatim}
Item pop and push operations are most commonly-used manipulations for the state transition of stack. The auxiliary functions \texttt{push\_stack} and \texttt{pop\_stack} are defined to control the stack change. For the formalization of \texttt{Swap} instructions, two recursive functions \texttt{fetch} and \texttt{drop} are defined to manipulate lists and one main function \texttt{swap\_stack} that implements the stack swap instruction is defined further based on these two functions.
With the pre-defined auxiliary functions, the definition of the interpreter function is essentially comprised of component update of the machine state with regard to concrete instructions.

\subsection{OCaml Extraction and Rust Connection}
We customizedly defined a series of drivers to extract from WhyML programs to Ocaml programs.

\section{Experiment and Analysis}\label{Sec: Experiment}
We have presented the formal implementation of EVM in Why3, based on which important properties can be verified through automatic and interactive theorem provers. We proceed to test our executable OCaml implementation extracted from WhyML against the standard test suite. 
\section{Related Work}\label{Sec: Related}0
The research interest of using blockchain technology has exploded since the inception  of Bitcoin. As the popularity of the second generation blockchain Ethereum grows, a series of security vulnerabilities has also appeared. Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units between different parties, the security of contract programs and EVM implementations is of paramount importance. To address the security challenges, researchers resort to the techniques of formal methods and program analysis.

\begin{itemize}
    \item \textbf{Formalization Foundation of EVM} An executable formal semantics of EVM have been created in K framework by Everett et al. \cite{hildenbrandt2017kevm}.  Hirai \cite{hirai2017defining} proposed an EVM implementation in Lem, a language that can be compiled for a few interactive theorem provers, and further proved some safety properties of smart contracts in Isabelle/HOL. The \texttt{hevm} project\cite{hevm} is implemented in Haskell especially for unit testing and debugging smart contracts though the EVM implementation is not completed yet. Besides the above formalizations of EVM, there are also implementations of EVM in Ruby\cite{cryptape}, Javascript\cite{vmjs}, Go\cite{vmgo} and etc.
    \item \textbf{Verification of Smart Contracts} Sergey et al. \cite{sergey2017concurrent} provides a new perspective between smart contracts and concurrent objects, based on which existing tools and insights for understanding, debugging and verifying concurrent objects can be used on smart contract behaviors. \cite{luu2016making} pointed out several new security problems and proposed a way to enhance the operational semantics of Ethereum to make smart contracts less vulnerable. Due to the difficulty of correcting the semantics of Ethereum, Luu et al.\cite{luu2016making} also implements a symbolic execution tool \texttt{OYENTE} to find security bugs. A framework to analyze and verify both the runtime safety and the functional correctness of Solidity contracts in F* was presented in \cite{bhargavan2016formal}.
\end{itemize}

\section{Conclusion and Future Work}\label{Sec: Conclusion}

\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
%%%justified by the macro package automatically.} 
\label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{the}
%
%
\end{document}

### 2020-04-25 COORDINATION2020/paper2.tex
paper6 update

--- 2020-04-25 COORDINATION2020/paper.tex
@@
 %
+\usepackage{epsfig}
+\usepackage{amsmath}
+\usepackage{amscd}
+\usepackage{amssymb}
+\usepackage{epsf}
 \usepackage{graphicx}
+%\usepackage{times}
+\usepackage{stmaryrd}
+\usepackage{latexsym}
+\usepackage{mathrsfs}
+\usepackage[english]{babel}
+\usepackage[latin1]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{listings}
+\usepackage{fancyvrb}
+\usepackage{fancybox}
+\usepackage{algorithmic}
+\usepackage{algorithm}
+\usepackage{color}
+\usepackage{tikz}
+\usepackage{reotex}
+\usepackage{multicol}
+\usepackage{multirow}
+\usepackage{varwidth}
+\usepackage{tabularx}
 \usepackage{verbatim}
@@
 \title{Towards a Formally Verified EVM in Production Environment}
+\titlerunning{Towards a Formally Verified EVM in Production Environment}
+
 %
@@
 }
+\authorrunning{X.~Zhang, Y.~Li and M.~Sun}
 %
@@
 \subsection{Why3}
-Why3\cite{filliatre2013why3} is a tool for deductive program verification.
+Why3~\cite{filliatre2013why3} is a tool for deductive program verification.
 It provides a standard library of logical theories, such as integer and real arithmetic, and basic programming data structures, such as arrays and queues.
@@
 The program code of the contract is fixed after deployment and it will be invoked whenever it receives a transaction.
+
 \section{EVM Framework}\label{Sec: Framework}
-\subsection{Methodology of EVM Framework}
-This framework can be considered as an experiment in a methodology that combines verification and testing for developing secure EVM implementations, and also as a tool for verifying smart contracts after compiling into bytecodes.
-Figure TOREF outlines the whole framework for developing a formally verified EVM in production environment.
+%\subsection{Methodology of EVM Framework}
+In this section, we demonstrate the EVM framework in detail. The main idea of the framework is to combine verification and testing towards developing secure EVM implementations.
+It also provides the potential to verify smart contracts at the bytecode level.
+This framework is mainly comprised of two parts: EVM specification in Why3 and experimental testing based on OCaml Extraction and Rust connection.
+This approach leverages on the formal methods and engineering, allowing us to perform both rigorous verification and efficient testing for EVM implementations and further smart contracts.
+
 \subsection{EVM in Why3}
-According to the Ethereum project yellow paper\cite{wood2014ethereum}, we translated EVM into Why3, which provides a programming and specification language WhyML.
-Based on the EVM definitions, Why3 further generates verification conditions according to the property specification, and allows the users to split the goals into different subgoals and prove each subgoal through different Satisfiability Modulo Theories (SMT) solvers.
+The first phase of the framework is to define a formal specification of EVM in Why3 and provide a platform for rigorous verification.  
+We develop the EVM specification, following the Ethereum project yellow paper~\cite{wood2014ethereum}.
+More specifically, the EVM implementation is translated into WhyML, the programming and specification language of Why3.
+Towards the verification, verification conditions can be further generated through Why3, based on the EVM and property specification.
+The verification goals will then be split into a set of subgoals or directly be proved through the supported Satisfiability Modulo Theories (SMT) solvers.
 In cases when the automatic SMT slovers cannot deal with, users can resort to interactive theorem proves based on the files generated by Why3.
 
-As have been mentioned before, EVM is a simple stack-based machine.
+EVM is essentially a simple stack-based machine.
 The memory model of EVM is a word-addressed byte array, which is volatile.
 The storage model of EVM is a non-volatile word-addressed word array.
-The perspective we see the execution process of a sequence of opcodes (instructions), which could be complied from a smart contract, is as a state transition process and it finally leads to a series of changes in the stack, memory and etc.
+The above three components form the infrastructure of EVM.
+Based on the formalization of the infrastructure, the most important is to capture the execution result of the EVM instructions.
+The perspective from which we deal with the execution process of a sequence of opcodes (instructions) is as a state transition process.
+This process starts with a initial state and leads to a series of changes in the stack, memory and etc.
+The formalization of base infrastructure and the instruction set are specified through \textit{Type Definition} and \textit{Instruction Definition}, respectively.
+\textit{Interpreter Definition} provides the specification of the interpreter and auxiliary functions.
 
-\subsubsection{Type Definition}
-Based on the needs of type requirements of Ethereum, such as that the machine word of EVM is 256 bits and the address is 160 bits, we developed a series of type modules \texttt{UInt256}, \texttt{UInt160} and etc.
-to ease the representation of the corresponding types in Ethereum.
-Why3 also supports type alias which makes the source code in WhyML more readable.
-Stack is defined as a list of elements whose type are \texttt{uint256}, aliased by \texttt{machword}.
-Memory is defined as a function that maps \texttt{machword} to an option type \texttt{option memory\_content}.
-The \texttt{memory\_content} is an enumeration type including \texttt{Item8} and \texttt{Item256} since the memory content could be accessed through 256-bit store and 8-bit store instructions.
-Storage is defined as a function that maps \texttt{machword} to \texttt{machword}.
-There are also other enumeration types defined to reflect the virtual machine status, the operation error, and a big view of the returned result which are \texttt{vmstatus}, \texttt{error} and \texttt{return\_type}.
-The record type \textt{machine\_state} represents the machine state whose components contain stack, memory, program counter, vmstatus, the instruction list and etc..
+\subsubsection{Type Definition}\label{sec:type}
 
-\subsubsection{Instruction Definition}
-Inspired by the instruction formalization of EVM in Lem \cite{hirai2017defining}, we defined the instruction set in different groups, such as arithmetic operations, stack operations and etc., then integrated them into a final type definition.
-The final instruction type definition is presented as follows, which shows the different instruction groups:
+To formalize the infrastructure of EVM, we first need to provide the formalization of some commonly-used types in EVM, such as the types of machine word and the address in EVM.
+Hence, we developed a series of type modules \texttt{UInt256}, \texttt{UInt160} and etc.
+to ease the representation of corresponding types in EVM.
+We also use type alias supported by Why3 to make the basic formalization more readable and consistent with the original definition.
+
+To this end, the components of the base infrastructure can be specified.
+Stack is defined as a list of elements whose type is \texttt{uint256}, aliased by \texttt{machine word}.
+Memory is defined as a function that maps \texttt{machine word} to an option type \texttt{option memory\_content}.
+Since the memory content could be accessed through 256-bit store and 8-bit store instructions, \texttt{memory\_content} is defined as an enumeration type including \texttt{Item8} and \texttt{Item256}.
+Similarly, Storage is defined as a function that maps \texttt{machine word} to \texttt{machine word}.
+To reflect the implicit change of the machine state, we defined more miscellaneous types.
+For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to capture the virtual machine status, the operation error, and the view of the returned result.
+The record type \texttt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list and etc.
+
+\subsubsection{Instruction Definition}\label{sec:instruction}
+The infrastructure has been built to specify the state of the virtual machine.
+Here we present the formal specification of the action set, i.e., the instruction set.
+Inspired by the instruction formalization in Lem~\cite{hirai2017defining}, we defined the instruction set in multiple groups, such as arithmetic operations, stack operations and etc., then integrated them into a summarized type definition \texttt{instruction}.
+The definition of \texttt{instruction} is presented as follows, where different subsets of instructions are wrapped up to form the complete specification.
 \begin{verbatim}
@@
 \end{verbatim}
-The organization of the instruction group is a bit different from the yellow paper\cite{wood2014ethereum}.
-The comparison operations are contained in the arithmetic operations \texttt{Arith} and the comparison operations for signed arithmetic are contained in the signed arithmetic operations \texttt{Sarith}, respectively.
-The bitwise operations and \texttt{BYTE} operation are included in the bit-related instructions \texttt{Bits}.
-Almost all of the information related instructions including environmental and block information are defined in type \texttt{info\_inst}, except some \texttt{CALL} and \texttt{CODE} instructions like the \texttt{CALLDATACOPY}, \texttt{CODECOPY} and \texttt{CALLDATALOAD} which are closely related to memory and stack.
-Therefore, for the memory and stack instruction groups, some extra instructions are added to the original instruction subsets presented in the yellow paper.
-In case when there exists some instruction that is illegal, the instruction \texttt{Invalid} is included in the instruction type definition.
-The \texttt{STOP} operation and the system operations from the yellow paper except \texttt{Invalid} are contained in the \textit{System} instruction set.
-As for the remaining instruction groups, they are basically the same as the corresponding instruction subsets in \cite{wood2014ethereum}.
-\subsubsection{Interpreter Definition}
-The function interpreter maps from some machine state to a new machine state, mainly in charge of formalizing the state transition result of different instructions.
-In order to make the definition of interpreter more concise, we defined some auxiliary functions.
-For example, the following function is used to obtain the instruction which needs to be executed from the instruction list according to the program counter.
+
+The organization of the instruction category is a bit different from the yellow paper~\cite{wood2014ethereum}.
+The comparison operations are grouped in the arithmetic operation set \texttt{Arith}; and the comparison operations for signed arithmetic are included in the signed arithmetic operation set \texttt{Sarith}.
+The bitwise operations and operation \texttt{BYTE} are categorized into the bit-related instruction group \texttt{Bits}.
+The information related instructions including environmental and block information ones are defined in type \texttt{info\_inst}, except \texttt{CALL} and \texttt{CODE} instructions, such as \texttt{CALLDATACOPY}, \texttt{CODECOPY}, \texttt{CALLDATALOAD} and etc.
+These instructions are more closely related to memory and stack status.
+Therefore, extra instructions but closely-related ones are added to the original memory and stack instruction groups presented in the yellow paper.
+In case when some illegal command occurs, the instruction \texttt{Invalid} is included in the \texttt{instruction} definition.
+The \texttt{STOP} operation and the system operations from the yellow paper are defined in the \texttt{System} instruction set.
+The specification of the remaining instruction groups are basically the same as the corresponding instruction subsets in \cite{wood2014ethereum}.
+
+\subsubsection{Interpreter Definition}\label{sec:interpreter}
+The specification of \texttt{interpreter} formalizes the state transition result of different instructions.
+For a specific instruction, the interpreter determines the resultant machine status developing from the current status.
+To make the definition of the interpreter more concise and compact, we defined some auxiliary functions.
+For example, the following function is used to obtain the next instruction to be executed.
+It is obtained from the instruction list following the program counter.
 \begin{verbatim}
@@
 \end{verbatim}
-Item pop and push operations are most commonly-used manipulations for the state transition of stack.
-The auxiliary functions \texttt{push\_stack} and \texttt{pop\_stack} are defined to control the stack change.
-For the formalization of \texttt{Swap} instructions, two recursive functions \texttt{fetch} and \texttt{drop} are defined to manipulate lists and one main function \texttt{swap\_stack} that implements the stack swap instruction is defined further based on these two functions.
-With the pre-defined auxiliary functions, the definition of the interpreter function is essentially comprised of component update of the machine state with regard to concrete instructions.
 
-\subsection{OCaml Extraction and Rust Connection}
-We customizedly defined a series of drivers to extract from WhyML programs to Ocaml programs.
+Pop and push operations are most commonly-used manipulations for the state transition of stack.
+Auxiliary functions \texttt{push\_stack} and \texttt{pop\_stack} are defined to control the change of stack status.
+For capturing the status transition result of \texttt{Swap} instructions, recursive functions \texttt{fetch} and \texttt{drop} are defined to support more direct manipulation on lists.
+Function \texttt{swap\_stack} is defined further for state transition of swap instructions.
+With the pre-defined auxiliary functions, the definition of the interpreter function is essentially comprised of machine status update with regard to concrete instructions.
+
+\subsection{Experimental Testing}
+We customizedly defined a series of drivers to extract WhyML programs into Ocaml programs.
 
@@
 We proceed to test our executable OCaml implementation extracted from WhyML against the standard test suite.
-\section{Related Work}\label{Sec: Related}0
-The research interest of using blockchain technology has exploded since the inception  of Bitcoin.
-As the popularity of the second generation blockchain Ethereum grows, a series of security vulnerabilities has also appeared.
-Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units between different parties, the security of contract programs and EVM implementations is of paramount importance.
-To address the security challenges, researchers resort to the techniques of formal methods and program analysis.
+
+\section{Related Work}\label{Sec: Related}
+Research interest of blockchain technology has exploded since the inception  of Bitcoin.
+As the popularity of the second generation of blockchain, Ethereum, grows, a series of security vulnerabilities have also appeared.
+Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units among multiple parties, the security of smart contract programs and EVM implementations is of paramount importance.
+To address the security challenges, researchers resorted to the techniques of formal methods and program analysis.
 
 \begin{itemize}
-    \item \textbf{Formalization Foundation of EVM} An executable formal semantics of EVM have been created in K framework by Everett et al.
-\cite{hildenbrandt2017kevm}.
-Hirai \cite{hirai2017defining} proposed an EVM implementation in Lem, a language that can be compiled for a few interactive theorem provers, and further proved some safety properties of smart contracts in Isabelle/HOL.
-The \texttt{hevm} project\cite{hevm} is implemented in Haskell especially for unit testing and debugging smart contracts though the EVM implementation is not completed yet.
-Besides the above formalizations of EVM, there are also implementations of EVM in Ruby\cite{cryptape}, Javascript\cite{vmjs}, Go\cite{vmgo} and etc.
-    \item \textbf{Verification of Smart Contracts} Sergey et al.
-\cite{sergey2017concurrent} provides a new perspective between smart contracts and concurrent objects, based on which existing tools and insights for understanding, debugging and verifying concurrent objects can be used on smart contract behaviors.
-\cite{luu2016making} pointed out several new security problems and proposed a way to enhance the operational semantics of Ethereum to make smart contracts less vulnerable.
-Due to the difficulty of correcting the semantics of Ethereum, Luu et al.\cite{luu2016making} also implements a symbolic execution tool \texttt{OYENTE} to find security bugs.
+    \item \textbf{Formalization Foundation of EVM} An executable formal semantics of EVM has been created in K framework by Everett et al.~\cite{hildenbrandt2017kevm}.
+Hirai~\cite{hirai2017defining} proposed an EVM implementation in Lem, a language that can be compiled for a few interactive theorem provers.
+Further, safety properties of smart contracts can be proved in proof assistants like Isabelle/HOL.
+The \texttt{hevm} project~\cite{hevm} is implemented in Haskell for unit testing and debugging smart contracts, though the EVM implementation is not completed yet.
+Besides the above formalizations of EVM, there are also implementations of EVM in Javascript~\cite{vmjs}, Go~\cite{vmgo}, Ruby~\cite{cryptape} and etc.
+    \item \textbf{Verification of Smart Contracts} Sergey et al.~\cite{sergey2017concurrent} provided a new perspective between smart contracts and concurrent objects, based on which existing tools and insights for understanding, debugging and verifying concurrent objects can be used on smart contract behaviors.
+In \cite{luu2016making}, several new security problems were pointed out and a way to enhance the operational semantics of Ethereum was proposed to make smart contracts less vulnerable.
+Due to the difficulty of correcting the semantics of Ethereum, Luu et al.~\cite{luu2016making} also implemented a symbolic execution tool \texttt{OYENTE} to find security bugs.
 A framework to analyze and verify both the runtime safety and the functional correctness of Solidity contracts in F* was presented in \cite{bhargavan2016formal}.
@@
 \section{Conclusion and Future Work}\label{Sec: Conclusion}
-
-\subsection{A Subsection Sample}
-Please note that the first paragraph of a section or subsection is
-not indented. The first paragraph that follows a table, figure,
-equation etc. does not need an indent, either.
-
-Subsequent paragraphs, however, are indented.
-
-\subsubsection{Sample Heading (Third Level)} Only two levels of
-headings should be numbered. Lower level headings remain unnumbered;
-they are formatted as run-in headings.
-
-\paragraph{Sample Heading (Fourth Level)}
-The contribution should contain no more than four levels of
-headings. Table~\ref{tab1} gives a summary of all heading levels.
-
-\begin{table}
-\caption{Table captions should be placed above the
-tables.}\label{tab1}
-\begin{tabular}{|l|l|l|}
-\hline
-Heading level &  Example & Font size and style\\
-\hline
-Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-\hline
-\end{tabular}
-\end{table}
-
-\noindent Displayed equations are centered and set on a separate
-line.
-\begin{equation}
-x + y = z
-\end{equation}
-Please try to avoid rasterized images for line-art diagrams and
-schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig1}).
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-%%%justified by the macro package automatically.} 
-\label{fig1}
-\end{figure}
-
-\begin{theorem}
-This is a sample theorem. The run-in heading is set in bold, while
-the following text appears in italics. Definitions, lemmas,
-propositions, and corollaries are styled the same way.
-\end{theorem}
-%
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%
-\begin{proof}
-Proofs, examples, and remarks have the initial word in italics,
-while the following text appears in normal font.
-\end{proof}
 

### 2020-04-25 COORDINATION2020/paper3.tex
paper6 update

--- 2020-04-25 COORDINATION2020/paper2.tex
@@
 %
-\usepackage{epsfig}
-\usepackage{amsmath}
-\usepackage{amscd}
-\usepackage{amssymb}
-\usepackage{epsf}
 \usepackage{graphicx}
-%\usepackage{times}
-\usepackage{stmaryrd}
-\usepackage{latexsym}
-\usepackage{mathrsfs}
-\usepackage[english]{babel}
-\usepackage[latin1]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{listings}
-\usepackage{fancyvrb}
-\usepackage{fancybox}
-\usepackage{algorithmic}
-\usepackage{algorithm}
-\usepackage{color}
-\usepackage{tikz}
-\usepackage{reotex}
-\usepackage{multicol}
-\usepackage{multirow}
-\usepackage{varwidth}
-\usepackage{tabularx}
 \usepackage{verbatim}
@@
 \title{Towards a Formally Verified EVM in Production Environment}
-\titlerunning{Towards a Formally Verified EVM in Production Environment}
-
 %
@@
 }
-\authorrunning{X.~Zhang, Y.~Li and M.~Sun}
 %
@@
 \begin{abstract}
-Among dozens of decentralized computing platforms, Ethe\-reum attracts widespread attention for its native support of smart contracts by means of a virtual machine called EVM.
-Programs can be developed in various front-end languages.
-For example, Solidity can be deployed to the blockchain in the form of compiled EVM opcodes.
-However, such flexibility leads to critical safety challenges.
+Among dozens of decentralized computing platforms, Ethereum attracts widespread attention for its native support of smart contracts by means of a virtual machine called EVM.
+Programs written in various front-end languages, Solidity, for example, can be deployed to the blockchain in form of compiled EVM opcodes.
+However, such flexibility also leads to safety challenges.
 In this paper, we formally define the behavior of EVM in Why3, a platform for deductive program verification, which facilitates the verification of different properties.
@@
 For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to capture the virtual machine status, the operation error, and the view of the returned result.
-The record type \texttt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list and etc.
+The record type \textt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list and etc.
 
@@
 Therefore, extra instructions but closely-related ones are added to the original memory and stack instruction groups presented in the yellow paper.
-In case when some illegal command occurs, the instruction \texttt{Invalid} is included in the \texttt{instruction} definition.
+In case when some illegal command occurs, the instruction \texttt{Invalid} is included in the \textt{instruction} definition.
 The \texttt{STOP} operation and the system operations from the yellow paper are defined in the \texttt{System} instruction set.
@@
 
-\subsection{Experimental Testing}
-We customizedly defined a series of drivers to extract WhyML programs into Ocaml programs.
+\subsection{Running EVM in Production Environment}
+%We customizedly defined a series of drivers to %extract WhyML programs into Ocaml programs. 
+In this section, we introduce the second phase of the framework: deploy the verified EVM, encoded in Why3, in production environments.
+The deployment is essentially based on a co-compilation framework between OCaml and Rust.
 
-\section{Experiment and Analysis}\label{Sec: Experiment}
-We have presented the formal implementation of EVM in Why3, based on which important properties can be verified through automatic and interactive theorem provers.
-We proceed to test our executable OCaml implementation extracted from WhyML against the standard test suite.
+OCaml is a functional programming language where the programs can be compiled either to OCaml bytecode or executable binaries.
+In the latter case, a runtime library is attached to handle various non-functional features like memory management.
+Through the \texttt{Callback} module, OCaml allows us to register a set of callback functions which can be used as an interface in static or dynamic linking.
+So we first defined a series of customized drivers to extract WhyML programs into Ocaml programs.
+After the extraction, the OCaml implementation of EVM is then encapsulated and exposed as a static linked library.
+This library can be further called by the EVM host in Rust.
+
+The framework provides the interaction mechanism between Rust, the productive programming language, and Why3 the formal specification language.
+By gluing them together, verified models can be directly executed in production environments for further testing.
 
@@
 As the popularity of the second generation of blockchain, Ethereum, grows, a series of security vulnerabilities have also appeared.
-Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units among multiple parties, the security of smart contract programs and EVM implementations is of paramount importance.
+Since EVM and smart contracts deal directly with the transactions of valuable c
+ryptocurrency units among multiple parties, the security of smart contract programs and EVM implementations is of paramount importance.
 To address the security challenges, researchers resorted to the techniques of formal methods and program analysis.

### 2020-04-25 COORDINATION2020/paper4.tex
paper6 update

--- 2020-04-25 COORDINATION2020/paper3.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
 \documentclass[runningheads]{llncs}
-%
+
+\usepackage{epsfig}
+\usepackage{amsmath}
+\usepackage{amscd}
+\usepackage{amssymb}
+\usepackage{epsf}
 \usepackage{graphicx}
+%\usepackage{times}
+\usepackage{stmaryrd}
+\usepackage{latexsym}
+\usepackage{mathrsfs}
+\usepackage[english]{babel}
+\usepackage[latin1]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{listings}
+\usepackage{fancyvrb}
+\usepackage{fancybox}
+\usepackage{algorithmic}
+\usepackage{algorithm}
+\usepackage{color}
+\usepackage{tikz}
+\usepackage{reotex}
+\usepackage{multicol}
+\usepackage{multirow}
+\usepackage{varwidth}
+\usepackage{tabularx}
 \usepackage{verbatim}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
 \usepackage{url}
+
+\input{common}
+\long\def\CUT#1{\marginpar{CUT}} \long\def\CUT#1{\relax}
+
 \begin{document}
-%
 \title{Towards a Formally Verified EVM in Production Environment}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
+\titlerunning{Towards a Formally Verified EVM in Production Environment}
+
 \author{Xiyue Zhang\inst{1} \and
@@
 }
-%
-% \authorrunning{F. Author et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
+\authorrunning{X.~Zhang, Y.~Li and M.~Sun}
+
 \institute{School of Mathematical Sciences, Peking University
@@
 \email{\{xiyuezhang, liyi\_math, sunm\}@pku.edu.cn}}
-%
+
 \maketitle              % typeset the header of the contribution
-%
+
 \begin{abstract}
-Among dozens of decentralized computing platforms, Ethereum attracts widespread attention for its native support of smart contracts by means of a virtual machine called EVM.
-Programs written in various front-end languages, Solidity, for example, can be deployed to the blockchain in form of compiled EVM opcodes.
-However, such flexibility also leads to safety challenges.
+Among dozens of decentralized computing platforms, Ethe\-reum attracts widespread attention for its native support of smart contracts by means of a virtual machine called EVM.
+Programs can be developed in various front-end languages.
+For example, Solidity can be deployed to the blockchain in the form of compiled EVM opcodes.
+However, such flexibility leads to critical safety challenges.
 In this paper, we formally define the behavior of EVM in Why3, a platform for deductive program verification, which facilitates the verification of different properties.
@@
 \end{abstract}
-%
-%
-%
+
 \section{Introduction}
-Ever since the inception of the Bitcoin \cite{nakamoto2008bitcoin} blockchain system, cryptocurrencies have become a global revolutionary phenomenon known to majority of people.
-Meanwhile, the decentralized system with no server or central authority, which emerges as a side product of Bitcoin, shows great potential in carrying out secure online transactions.
-From then until now, there have been so much change and growth on blockchain technology.
-The researchers and developers see plenty of potential and massive possibilities of blockchain applications, especially in financial, governmental services.
-Ethereum\cite{Ethereum} extends Bitcoin's design, which can not only process transactions but also process complex smart contracts and programs.
+
+Ever since the inception of the Bitcoin blockchain system \cite{nakamoto2008bitcoin}, cryptocurrencies have become a well-known global revolutionary phenomenon.
+Meanwhile, the decentralized blockchain system with no server or central authority, which emerges as a side product of Bitcoin and provides a continuously growing ledger of transactions being represented as a chained list of blocks distributed and maintained over a peer-to-peer network \cite{ZXDCW18}, shows great potential in carrying out secure online transactions.
+From then on, there have been a lot of changes and growth on the blockchain technology.
+%The researchers and developers see plenty of potential and massive possibilities of blockchain applications, especially in financial, governmental services.
+Ethereum \cite{Ethereum} extends Bitcoin's design, which can process not only transactions but also complex programs and {\em smart contracts}.
+Smart contracts can automatically run inside a blockchain,
+making it possible to use blockchain techniques in many other application domains besides cryptocurrencies, and has attracted a lot of attention from government, finance, health, entertainment and industry.
 This feature makes Ethereum a popular ecosystems for building blockchain-applications, which gains much more interest to innovate the options to utilize blockchain.
 
-Smart contracts are often written in a high level programming language called \textit{Solidity} \cite{solidity} and then compiled into low-level machine instructions (\textit{opcodes}), which is encoded into bytecode.
+%Different languages have been proposed for developing smart contracts. For example, Ethereum provides a Turing-complete programming language named {\em Solidity} to implement smart contracts.
+Smart contracts are often written in a Turing-complete programming language called \textit{Solidity} \cite{solidity} and then compiled into low-level machine instructions (\textit{opcodes}), which can be encoded into bytecode.
 Ethereum Virtual Machine (EVM) is a quasi-Turing complete machine which implements the execution model of the Ethereum.
@@
 However, EVM and smart contracts are faced with several security vulnerabilities.
-Atzei et al.
-presented a taxonomy of vulnerabilities and related attacks against Solidity, the EVM, and the blockchain in \cite{atzei2016survey}.
-The adoption of formal methods can facilitate the production of trustworthy and reliable software systems.
+In fact, a lot of attacks on smart contracts succeeded in the past years, such as the famous DAO (Decentralized Autonomous Organization) attack in 2016 resulting in the lost of more than 60M USD, and the Parity Wallet Hacks in which vulnerabilities in the wallet was exploited by an attacker to successfully steal over 150,000 ETH (about 30M USD), and leads to more than 250M USD frozen later in 2017.
+A taxonomy of vulnerabilities and related attacks against Solidity, the EVM, and the blockchain is presented in \cite{atzei2016survey}.
+
+%The adoption of formal methods can facilitate the production of trustworthy and reliable software systems.
 Verification such as theorem proving techniques and testing have become essential to guarantee the correctness of safety-critical systems.
 
-To address the security challenges against EVM, we present a framework of generating formally verified EVM for production environment in this paper.
-The contributions of this work are: Firstly, a formal definition of EVM is specified in WhyML, the language of programming and specification in Why3.
-Secondly, an implementation of EVM in OCaml is generated through an extraction mechanism based on a series of customized drivers.
-Lastly, the verification of sample properties and testing of the OCaml implementation for EVM against a standard test suite for Ethereum.
+%Developing trustworthy smart contracts is a very challenging task due to the complexity of the distributed execution environment and programming languages.
+In fact, a lot of attacks on smart contracts succeeded in the past years, such as the famous DAO (Decentralized Autonomous Organization) attack in 2016 resulting in the lost of more than 60M USD, and the Parity Wallet Hacks in which vulnerabilities in the wallet was exploited by an attacker to successfully steal over 150,000 ETH (about 30M USD), and leads to more than 250M USD frozen later in 2017.
 
-This paper is organized as follows: Section \ref{Sec: Pre} presents some background about Why3, Ethereum Virtual Machine (EVM) and smart contracts.
+Formal verification techniques such as theorem proving and testing have become essential to guarantee the correctness of systems.
+The adoption of formal methods can facilitate the production of trustworthy and reliable smart contracts as well.
+To deal with the security challenges against EVM, we present a formal framework of generating verified EVM for production environment in this paper. The contributions of this work are: 
+\begin{itemize}
+\item A formal definition of EVM specified in WhyML, the programming and specification language used in Why3 \cite{filliatre2013why3}. 
+\item An implementation of EVM in OCaml generated through an extraction mechanism based on a series of customized drivers. 
+\item The verification of sample properties and testing of the OCaml implementation for EVM against a standard test suite for Ethereum.
+\end{itemize}
+%In this paper we propose a framework for modeling and verification of smart contracts based on the Mediator language \cite{LS17} and the UPPAAL model checker \cite{BDLPY11}.
+There are some existing works for formal verification of smart contracts.
+\cite{AR18} provides a SMT based approach for verification of Solidity smart contracts.
+...
+%Comparing with the existing works, the new approach: benefits of Mediator for modeling smart contracts, automatic verification by translation to UPPAAL, probabilistic and statistical model checking ...
+
+This paper is organized as follows: %Section \ref{Sec: Pre} presents some background about Why3, Ethereum Virtual Machine (EVM) and smart contracts. 
 We outline the framework for formalizing, property verifying and testing of EVM in Section \ref{Sec: Framework}.
-Based on the framework, we perform some experiments in Section \ref{Sec: Experiment} and highlight th e verification and testing results for the properties of EVM.
-Section \ref{Sec: Related} presents some related work.
-Finally, we summarized this paper and point out the future research direction in Section \ref{Sec: Conclusion}.
+%Based on the framework, we perform some experiments in Section \ref{Sec: Experiment} and highlight the verification and testing results for the properties of EVM.
+Section \ref{Sec: Related} presents some related work. Finally, we summarized this paper and point out the future research direction in Section \ref{Sec: Conclusion}.
 
+\CUT{
 \section{Preliminary}\label{Sec: Pre}
@@
 
+}
+
 \section{EVM Framework}\label{Sec: Framework}
 %\subsection{Methodology of EVM Framework}
-In this section, we demonstrate the EVM framework in detail. The main idea of the framework is to combine verification and testing towards developing secure EVM implementations.
+In this section, we present the EVM framework in detail. The main idea is to combine verification and testing towards developing secure EVM implementations.
 It also provides the potential to verify smart contracts at the bytecode level.
@@
 More specifically, the EVM implementation is translated into WhyML, the programming and specification language of Why3.
-Towards the verification, verification conditions can be further generated through Why3, based on the EVM and property specification.
-The verification goals will then be split into a set of subgoals or directly be proved through the supported Satisfiability Modulo Theories (SMT) solvers.
-In cases when the automatic SMT slovers cannot deal with, users can resort to interactive theorem proves based on the files generated by Why3.
+%Towards the verification,
+Verification conditions can be further generated through Why3 based on the EVM and property specification.
+The verification goals can be split into a set of subgoals or directly be proved through the supported Satisfiability Modulo Theories (SMT) solvers.
+In cases when the automatic SMT solvers cannot deal with, users can resort to interactive theorem provers based on the files generated by Why3.
 
@@
 The perspective from which we deal with the execution process of a sequence of opcodes (instructions) is as a state transition process.
-This process starts with a initial state and leads to a series of changes in the stack, memory and etc.
+This process starts with an initial state and leads to a series of changes in the stack, memory etc.
 The formalization of base infrastructure and the instruction set are specified through \textit{Type Definition} and \textit{Instruction Definition}, respectively.
@@
 To formalize the infrastructure of EVM, we first need to provide the formalization of some commonly-used types in EVM, such as the types of machine word and the address in EVM.
-Hence, we developed a series of type modules \texttt{UInt256}, \texttt{UInt160} and etc.
-to ease the representation of corresponding types in EVM.
+Hence, we developed a series of type modules such as \texttt{UInt256} and \texttt{UInt160} to ease the representation of corresponding types in EVM.
 We also use type alias supported by Why3 to make the basic formalization more readable and consistent with the original definition.
@@
 For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to capture the virtual machine status, the operation error, and the view of the returned result.
-The record type \textt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list and etc.
+The record type \texttt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list, etc.
 
 \subsubsection{Instruction Definition}\label{sec:instruction}
-The infrastructure has been built to specify the state of the virtual machine.
-Here we present the formal specification of the action set, i.e., the instruction set.
-Inspired by the instruction formalization in Lem~\cite{hirai2017defining}, we defined the instruction set in multiple groups, such as arithmetic operations, stack operations and etc., then integrated them into a summarized type definition \texttt{instruction}.
-The definition of \texttt{instruction} is presented as follows, where different subsets of instructions are wrapped up to form the complete specification.
+The infrastructure has been built to specify the state of the virtual machine. %Here we present the formal specification of the action set, i.e., the instruction set. 
+Inspired by the instruction formalization in Lem~\cite{hirai2017defining}, we defined the instruction set in multiple groups, such as arithmetic operations and stack operations, then integrated them into a summarized type definition \texttt{instruction}.
+%The definition of \texttt{instruction} is presented as follows, where
+Different subsets of instructions are wrapped up to form the complete specification in the definition of \texttt{instruction}.
+\CUT{
 \begin{verbatim}
@@
 \end{verbatim}
+}
 
@@
 Therefore, extra instructions but closely-related ones are added to the original memory and stack instruction groups presented in the yellow paper.
-In case when some illegal command occurs, the instruction \texttt{Invalid} is included in the \textt{instruction} definition.
+In case when some illegal command occurs, the instruction \texttt{Invalid} is included in the \texttt{instruction} definition.
 The \texttt{STOP} operation and the system operations from the yellow paper are defined in the \texttt{System} instruction set.
@@
 
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
 \bibliographystyle{splncs04}
 \bibliography{the}
-%
-%
+
 \end{document}

### 2020-04-25 COORDINATION2020/paper5.tex
paper6 update

--- 2020-04-25 COORDINATION2020/paper4.tex
@@
 
-\author{Xiyue Zhang\inst{1} \and
-Yi Li\inst{1} \and
-Meng Sun\inst{1}
+\author{Xiyue Zhang,
+Yi Li and
+Meng Sun$^*$
 }
@@
 In this paper, we formally define the behavior of EVM in Why3, a platform for deductive program verification, which facilitates the verification of different properties.
-Furthermore, the extracted implementation in OCaml can be directly integrated into the production environment and tested against the standard test suite.
+The extracted implementation in OCaml can be directly integrated into the production environment and tested against the standard test suite.
 The combination of proofs and testing in our framework serves as a powerful analysis basis for EVM and smart contracts.
@@
 However, EVM and smart contracts are faced with several security vulnerabilities.
-In fact, a lot of attacks on smart contracts succeeded in the past years, such as the famous DAO (Decentralized Autonomous Organization) attack in 2016 resulting in the lost of more than 60M USD, and the Parity Wallet Hacks in which vulnerabilities in the wallet was exploited by an attacker to successfully steal over 150,000 ETH (about 30M USD), and leads to more than 250M USD frozen later in 2017.
+%In fact, a lot of attacks on smart contracts succeeded in the past years, such as the famous DAO (Decentralized Autonomous Organization) attack in 2016 resulting in the lost of more than 60M USD, and the Parity Wallet Hacks in which vulnerabilities in the wallet was exploited by an attacker to successfully steal over 150,000 ETH (about 30M USD), and leads to more than 250M USD frozen later in 2017.
 A taxonomy of vulnerabilities and related attacks against Solidity, the EVM, and the blockchain is presented in \cite{atzei2016survey}. 
-
-%The adoption of formal methods can facilitate the production of trustworthy and reliable software systems.
-Verification such as theorem proving techniques and testing have become essential to guarantee the correctness of safety-critical systems.
-
-%Developing trustworthy smart contracts is a very challenging task due to the complexity of the distributed execution environment and programming languages.
-In fact, a lot of attacks on smart contracts succeeded in the past years, such as the famous DAO (Decentralized Autonomous Organization) attack in 2016 resulting in the lost of more than 60M USD, and the Parity Wallet Hacks in which vulnerabilities in the wallet was exploited by an attacker to successfully steal over 150,000 ETH (about 30M USD), and leads to more than 250M USD frozen later in 2017.
-
-Formal verification techniques such as theorem proving and testing have become essential to guarantee the correctness of systems.
+%Formal verification techniques such as theorem proving and testing have become essential to guarantee the correctness of systems.
 The adoption of formal methods can facilitate the production of trustworthy and reliable smart contracts as well.
-To deal with the security challenges against EVM, we present a formal framework of generating verified EVM for production environment in this paper. The contributions of this work are: 
+To deal with the security challenges against EVM, we developed a formal framework of generating verified EVM for production environment in this paper. The contributions of this work are: 
 \begin{itemize}
@@
 %Based on the framework, we perform some experiments in Section \ref{Sec: Experiment} and highlight the verification and testing results for the properties of EVM.
-Section \ref{Sec: Related} presents some related work. Finally, we summarized this paper and point out the future research direction in Section \ref{Sec: Conclusion}.
+Section \ref{Sec: Related} presents some related work. Finally, we summarized this paper %and point out the future research direction 
+in Section \ref{Sec: Conclusion}.
 
@@
 
-To formalize the infrastructure of EVM, we first need to provide the formalization of some commonly-used types in EVM, such as the types of machine word and the address in EVM.
+To formalize the infrastructure of EVM, we need to provide the formalization of commonly-used types in EVM, such as the types of machine word and the address in EVM.
 Hence, we developed a series of type modules such as \texttt{UInt256} and \texttt{UInt160} to ease the representation of corresponding types in EVM.
-We also use type alias supported by Why3 to make the basic formalization more readable and consistent with the original definition.
+Type alias supported by Why3 are also used to make the basic formalization more readable and consistent with the original definition.
 
@@
 The bitwise operations and operation \texttt{BYTE} are categorized into the bit-related instruction group \texttt{Bits}.
-The information related instructions including environmental and block information ones are defined in type \texttt{info\_inst}, except \texttt{CALL} and \texttt{CODE} instructions, such as \texttt{CALLDATACOPY}, \texttt{CODECOPY}, \texttt{CALLDATALOAD} and etc.
+The information related instructions including environmental and block information ones are defined in type \texttt{info\_inst}, except \texttt{CALL} and \texttt{CODE} instructions, such as \texttt{CALLDATACOPY}, \texttt{CODECOPY} and \texttt{CALLDATALOAD}.
 These instructions are more closely related to memory and stack status.
-Therefore, extra instructions but closely-related ones are added to the original memory and stack instruction groups presented in the yellow paper.
+Therefore, extra instructions but closely-related ones are added to the original memory and stack instruction groups.
+% presented in the yellow paper.
 In case when some illegal command occurs, the instruction \texttt{Invalid} is included in the \texttt{instruction} definition.
@@
 Function \texttt{swap\_stack} is defined further for state transition of swap instructions.
-With the pre-defined auxiliary functions, the definition of the interpreter function is essentially comprised of machine status update with regard to concrete instructions.
+With these pre-defined auxiliary functions, the definition of the interpreter function is essentially comprised of machine status update with regard to concrete instructions.
 
@@
 %We customizedly defined a series of drivers to %extract WhyML programs into Ocaml programs. 
-In this section, we introduce the second phase of the framework: deploy the verified EVM, encoded in Why3, in production environments.
+We now introduce the second phase of the framework: deploy the verified EVM, encoded in Why3, in production environments.
 The deployment is essentially based on a co-compilation framework between OCaml and Rust.
@@
 
-The framework provides the interaction mechanism between Rust, the productive programming language, and Why3 the formal specification language.
+The framework provides the interaction mechanism between Rust and Why3.
 By gluing them together, verified models can be directly executed in production environments for further testing.
+The coupling between Rust and extracted OCaml implementation enables us to perform VM tests to test the basic workings of the verified VM.
+Information of the overarching environment is obtained through the interface of Rust implementation.
+The test can be performed on the execution of the OCaml implementations to check the operations in different transactions.
 
@@
 As the popularity of the second generation of blockchain, Ethereum, grows, a series of security vulnerabilities have also appeared.
-Since EVM and smart contracts deal directly with the transactions of valuable c
-ryptocurrency units among multiple parties, the security of smart contract programs and EVM implementations is of paramount importance.
+Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units among multiple parties, the security of smart contracts and EVM implementations is of paramount importance.
 To address the security challenges, researchers resorted to the techniques of formal methods and program analysis.
 
-\begin{itemize}
-    \item \textbf{Formalization Foundation of EVM} An executable formal semantics of EVM has been created in K framework by Everett et al.~\cite{hildenbrandt2017kevm}.
+%\begin{itemize}
+%    \item \textbf{Formalization Foundation of EVM} 
+An executable formal semantics of EVM has been created in K framework by Everett et al.~\cite{hildenbrandt2017kevm}.
 Hirai~\cite{hirai2017defining} proposed an EVM implementation in Lem, a language that can be compiled for a few interactive theorem provers.
@@
 The \texttt{hevm} project~\cite{hevm} is implemented in Haskell for unit testing and debugging smart contracts, though the EVM implementation is not completed yet.
-Besides the above formalizations of EVM, there are also implementations of EVM in Javascript~\cite{vmjs}, Go~\cite{vmgo}, Ruby~\cite{cryptape} and etc.
-    \item \textbf{Verification of Smart Contracts} Sergey et al.~\cite{sergey2017concurrent} provided a new perspective between smart contracts and concurrent objects, based on which existing tools and insights for understanding, debugging and verifying concurrent objects can be used on smart contract behaviors.
+Besides the above formalizations of EVM, there are also implementations of EVM in other languages such as %Javascript~\cite{vmjs},
+Go~\cite{vmgo} and Ruby~\cite{cryptape}.
+%    \item \textbf{Verification of Smart Contracts}
+
+Sergey et al.~\cite{sergey2017concurrent} provided a new perspective between smart contracts and concurrent objects, based on which existing tools and insights for understanding, debugging and verifying concurrent objects can be used on smart contract behaviors.
 In \cite{luu2016making}, several new security problems were pointed out and a way to enhance the operational semantics of Ethereum was proposed to make smart contracts less vulnerable.
@@
 A framework to analyze and verify both the runtime safety and the functional correctness of Solidity contracts in F* was presented in \cite{bhargavan2016formal}.
-\end{itemize}
+%\end{itemize}
 
-\section{Conclusion and Future Work}\label{Sec: Conclusion}
+\section{Conclusion}\label{Sec: Conclusion}
+We propose a framework to enable formal specification, verification and testing towards EVM.
+In this framework, the formalization of EVM is specified in WhyML, the programming and specification language of Why3.
+Based on the EVM formalization, automatic SMT solvers and interactive theorem provers provided in Why3 can be employed for verification.
+The OCaml implementation of EVM is extracted from the WhyML specification and then glued with Rust implementation based on the coupling framework.
+The coupling framework provides the interaction mechanism between OCaml and Rust, which allows us to perform tests on the new implementation without additional interface implementation.
+
+\subsection*{Acknowledgement}
+\noindent This work has been supported by the National Natural Science Foundation of China under grant no.
+61772038, 61532019 and 61272160, and the Guangdong Science and Technology Department (Grant no.2018B010107004).
 

### 2020-04-25 COORDINATION2020/paper6.tex
paper6 update

--- 2020-04-25 COORDINATION2020/paper5.tex
@@
 \documentclass[runningheads]{llncs}
+%\documentclass[conference]{IEEEtran}
 
@@
 \usepackage{color}
+% \usepackage{xcolor}
 \usepackage{tikz}
@@
 \usepackage{url}
+% \usepackage{tcolorbox}
+\newcommand {\xy} {\color{purple}}
+% \newcommand {\xy}[1]{\textcolor{purple}{{#1}}}
 
@@
 
-\author{Xiyue Zhang,
-Yi Li and
-Meng Sun$^*$
+%\author{\IEEEauthorblockN{Xiyue Zhang, Yi Li and Meng Sun}
+%\IEEEauthorblockA{School of Mathematical Sciences\\
+%Peking University\\
+%Beijing, China}
+%{\{xiyuezhang, liyi\_math, sunm\}@pku.edu.cn}}
+
+\author{Xiyue Zhang$^1$,
+Yi Li$^1$ and
+Meng Sun$^{1,2}$
 }
@@
 
-\institute{School of Mathematical Sciences, Peking University
+\institute{$^1$School of Mathematical Sciences, Peking University, Beijing, 100871, China
 \\
-\email{\{xiyuezhang, liyi\_math, sunm\}@pku.edu.cn}}
+$^2$Center for Quantum Computing, Peng Cheng Laboratory, Shenzhen, 518055, China
+\\
+\email{\{zhangxiyue, liyi\_math, sunm\}@pku.edu.cn}}
 
@@
 The combination of proofs and testing in our framework serves as a powerful analysis basis for EVM and smart contracts.
-
 \keywords{EVM \and Why3 \and Verification \and Testing.}
 \end{abstract}
+
+%\begin{keywords}
+%EVM, Why3, Verification, Testing
+%\end{keywords}
 
@@
 making it possible to use blockchain techniques in many other application domains besides cryptocurrencies, and has attracted a lot of attention from government, finance, health, entertainment and industry.
-This feature makes Ethereum a popular ecosystems for building blockchain-applications, which gains much more interest to innovate the options to utilize blockchain.
+This feature makes Ethereum a popular ecosystem for building blockchain-applications, which gains much more interest to innovate the options to utilize blockchain.
 
@@
 Smart contracts are often written in a Turing-complete programming language called \textit{Solidity} \cite{solidity} and then compiled into low-level machine instructions (\textit{opcodes}), which can be encoded into bytecode.
-Ethereum Virtual Machine (EVM) is a quasi-Turing complete machine which implements the execution model of the Ethereum.
-Given a sequence of bytecode instructions, which are compiled from smart contracts by EVM compiler, and the environment data, this execution model specifies how the blockchain transits from one state to another.
+Ethereum Virtual Machine (EVM) is a quasi-Turing complete machine which implements the execution model of the Ethereum Virtual Machine.
+Given a sequence of bytecode instructions, which are compiled from smart contracts by an EVM compiler, and the environment data, this execution model specifies how the blockchain transits from one state to another.
 
@@
 The adoption of formal methods can facilitate the production of trustworthy and reliable smart contracts as well.
-To deal with the security challenges against EVM, we developed a formal framework of generating verified EVM for production environment in this paper. The contributions of this work are: 
+To deal with the security challenges against EVM, we proposed a formal framework of generating verified EVM for production environment in this paper. The contributions of this work are: 
 \begin{itemize}
@@
 
-\section{EVM Framework}\label{Sec: Framework}
+\begin{figure*}[t]
+  \centering
+  \resizebox{0.8\textwidth}{!}{
+  \includegraphics{framework.pdf}
+  }
+  \caption{the Framework of Generating Verified EVM for Production Environment}
+  \label{fig:evm1}
+\end{figure*}
+
+\section{The Framework of Generating Verified EVM for Production Environment}\label{Sec: Framework}
 %\subsection{Methodology of EVM Framework}
-In this section, we present the EVM framework in detail. The main idea is to combine verification and testing towards developing secure EVM implementations.
+In this section, we present the framework of generating verified EVM for production environment in detail.
+The framework is as shown in Fig.
+\ref{fig:evm1} and the main idea is to combine verification and testing techniques towards developing secure EVM implementations.
 It also provides the potential to verify smart contracts at the bytecode level.
 This framework is mainly comprised of two parts: EVM specification in Why3 and experimental testing based on OCaml Extraction and Rust connection.
-This approach leverages on the formal methods and engineering, allowing us to perform both rigorous verification and efficient testing for EVM implementations and further smart contracts.
+This approach leverages on formal methods and engineering approaches, allowing us to perform both rigorous verification and efficient testing for EVM implementations and further smart contracts.
 
@@
 The storage model of EVM is a non-volatile word-addressed word array.
-The above three components form the infrastructure of EVM.
-Based on the formalization of the infrastructure, the most important is to capture the execution result of the EVM instructions.
+These three components form the infrastructure of EVM.
+Based on the formalization of the infrastructure, the most important aspect in this framework is to capture the execution result of the EVM instructions.
 The perspective from which we deal with the execution process of a sequence of opcodes (instructions) is as a state transition process.
@@
 The formalization of base infrastructure and the instruction set are specified through \textit{Type Definition} and \textit{Instruction Definition}, respectively.
-\textit{Interpreter Definition} provides the specification of the interpreter and auxiliary functions.
+And the \textit{Interpreter Definition} provides the specification of the interpreter and auxiliary functions.
 
@@
 
-To formalize the infrastructure of EVM, we need to provide the formalization of commonly-used types in EVM, such as the types of machine word and the address in EVM.
+To formalize the infrastructure of EVM, we need to first provide the formalization of commonly-used types in EVM, such as the types of machine words and the addresses in the EVM.
 Hence, we developed a series of type modules such as \texttt{UInt256} and \texttt{UInt160} to ease the representation of corresponding types in EVM.
@@
 
-To this end, the components of the base infrastructure can be specified.
+To this end, the components of the base infrastructure can be easily specified.
 Stack is defined as a list of elements whose type is \texttt{uint256}, aliased by \texttt{machine word}.
@@
 Since the memory content could be accessed through 256-bit store and 8-bit store instructions, \texttt{memory\_content} is defined as an enumeration type including \texttt{Item8} and \texttt{Item256}.
-Similarly, Storage is defined as a function that maps \texttt{machine word} to \texttt{machine word}.
+Similarly, storage is defined as a function that maps \texttt{machine word} to \texttt{machine word}.
 To reflect the implicit change of the machine state, we defined more miscellaneous types.
 For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to capture the virtual machine status, the operation error, and the view of the returned result.
-The record type \texttt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list, etc.
+Furthermore, the record type \texttt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list, etc.
 
@@
 The infrastructure has been built to specify the state of the virtual machine. %Here we present the formal specification of the action set, i.e., the instruction set. 
-Inspired by the instruction formalization in Lem~\cite{hirai2017defining}, we defined the instruction set in multiple groups, such as arithmetic operations and stack operations, then integrated them into a summarized type definition \texttt{instruction}.
+Inspired by the instruction formalization in Lem~\cite{hirai2017defining}, the instruction set is defined in multiple groups, such as {\em arithmetic operations} and {\em stack operations}, then these groups are integrated into a summarized type definition \texttt{instruction}.
 %The definition of \texttt{instruction} is presented as follows, where
@@
 For a specific instruction, the interpreter determines the resultant machine status developing from the current status.
-To make the definition of the interpreter more concise and compact, we defined some auxiliary functions.
+Some auxiliary functions are defined
+to make the definition of the interpreter more concise and compact.
 For example, the following function is used to obtain the next instruction to be executed.
@@
 
-Pop and push operations are most commonly-used manipulations for the state transition of stack.
+Pop and push operations are the most commonly-used manipulations for the state transition of stack.
 Auxiliary functions \texttt{push\_stack} and \texttt{pop\_stack} are defined to control the change of stack status.
 For capturing the status transition result of \texttt{Swap} instructions, recursive functions \texttt{fetch} and \texttt{drop} are defined to support more direct manipulation on lists.
-Function \texttt{swap\_stack} is defined further for state transition of swap instructions.
+Another function \texttt{swap\_stack} is defined further for state transition of swap instructions.
 With these pre-defined auxiliary functions, the definition of the interpreter function is essentially comprised of machine status update with regard to concrete instructions.
 
+\begin{figure*}[t]
+  \centering
+  \resizebox{0.8\textwidth}{!}{
+  \includegraphics{runninginPE.pdf}
+  }
+  \caption{Running EVM in Production Environment}
+   \label{fig2}
+\end{figure*}
+
 \subsection{Running EVM in Production Environment}
-%We customizedly defined a series of drivers to %extract WhyML programs into Ocaml programs. 
-We now introduce the second phase of the framework: deploy the verified EVM, encoded in Why3, in production environments.
+%We customizedly defined a series of drivers to %extract WhyML programs into OCaml programs. 
+Fig.
+\ref{fig2} shows the second phase of the framework: deploy the verified EVM, encoded in Why3, in production environments.
 The deployment is essentially based on a co-compilation framework between OCaml and Rust.
@@
 Through the \texttt{Callback} module, OCaml allows us to register a set of callback functions which can be used as an interface in static or dynamic linking.
-So we first defined a series of customized drivers to extract WhyML programs into Ocaml programs.
+So we first defined a series of customized drivers to extract WhyML programs into OCaml programs.
 After the extraction, the OCaml implementation of EVM is then encapsulated and exposed as a static linked library.
@@
 
+Rust is a multi-paradigm system programming language which is designed to provide better memory safety while maintaining high performance \cite{LBHN16}.
 The framework provides the interaction mechanism between Rust and Why3.
@@
 The coupling between Rust and extracted OCaml implementation enables us to perform VM tests to test the basic workings of the verified VM.
-Information of the overarching environment is obtained through the interface of Rust implementation.
-The test can be performed on the execution of the OCaml implementations to check the operations in different transactions.
+Information of the overarching environment is obtained through the interface of Rust implementation, and the test can be performed on the execution of the OCaml implementations to check the operations in different transactions.
+
+\subsection{Examples of Property Verification and Tests}
+{\xy
+In this section, we present some examples of property verification towards smart contracts and tests against Ethereum 
+test suites. 
+Specifically, we present the specification and verification of \emph{SafeMath} library and \emph{SimpleAuction} contract.
+For the tests, we perform the testing of arithematic operations against the Ethereum test suite.
+
+Generally, the central design choice of the framework is to leverage the infrastructure of 
+Why3, the deductive verification platform where a set of external theorem provers, both automated and interactive, 
+can be relied on to discharge verification conditions. At the same time, 
+OCaml programs can be directly extracted from WhyML programs through the extraction mechanism for further tests.
+}
+{\xy
+\paragraph{Overflow/Underflow property verification.}
+We first take the example of \emph{SafeMath} from Solidity 
+library. Overflow/Underflow problems often occur when we deal with number operations. For EVM, the unsigned interger type we 
+perform arithematic operations on range from 0 to $2^{256}$, which is specified as \texttt{uint256} in the WhyML specification.
+The properties we verify are to guarantee that overflow and underflow problems would not occur in the number operations.
+Besides, the correctness of the operation results are also specified in the postconditions and further verified, for example,
+the last postcondition in the function \texttt{div\_safe}.
+
+As can be seen from the following definition of \texttt{div\_safe},
+the function body is comprised of three parts, as a Hoare triple, 
+preconditions, program expressions and postconditions.
+The first precondition expresses that the divisor should be greater than
+zero. The first postcondition states that the returned value should
+satisfy the required property with no underflow issues. The other
+two postconditions are to guarantee the operation result correctness. 
+\begin{verbatim}
+let div_safe (a:uint256) (b:uint256): uint256
+requires {to_int b > 0}
+ensures {to_int result >= 0}
+ensures {to_int a = 0 -> to_int result = 0}
+ensures {to_int a <> 0 -> 
+to_int a = (to_int result) * (to_int b) + mod (to_int a) (to_int b)}
+= a / b
+\end{verbatim}
+
+We now proceed to the verification of the properties. The verification conditions can be obtained 
+through running \texttt{why3 prove} on the WhyML file. 
+The proving goals for \texttt{div\_safe} are derived as follows:
+
+\begin{verbatim}
+goal VC div_safe :
+forall a:uint256, b:uint256.
+  to_int b > 0 -> (not b = 0 && in_bounds (div a b)) /\
+  (forall result:uint256. result = div a b -> to_int result >= 0 &&
+  (to_int a = 0 -> to_int result = 0) &&
+  (not to_int a = 0 ->
+  to_int a = ((to_int result * to_int b) + mod (to_int a) (to_int b))))
+\end{verbatim}
+To prove the goals, we first apply the \texttt{split VC} transformation and 
+then call theorem provers \emph{alt-ergo} and \emph{cvc4} 
+to prove the subgoals automatically. The proof session state will be 
+stored in an XML file, which includes the proved WhyML file, the applied
+transformations, the used provers and the proof results.
+Complete proving goals derived from the functions and 
+proof sessions can be found on this website.
+}
+
+{\xy
+\paragraph{Simple Auction contract verification}
+
+}
 
 \section{Related Work}\label{Sec: Related}
+{\xy About comparison with KEVM framework with the support
+of ...logic, Hoare logic serves as a good framework for
+verification condition specification avoiding the complex definitions
+of the operational semantics.}
+
 Research interest of blockchain technology has exploded since the inception of Bitcoin.
@@
 %    \item \textbf{Formalization Foundation of EVM} 
-An executable formal semantics of EVM has been created in K framework by Everett et al.~\cite{hildenbrandt2017kevm}.
+An executable formal semantics of EVM has been created in the K framework by Everett et al.~\cite{hildenbrandt2017kevm}.
 Hirai~\cite{hirai2017defining} proposed an EVM implementation in Lem, a language that can be compiled for a few interactive theorem provers.
@@
 Due to the difficulty of correcting the semantics of Ethereum, Luu et al.~\cite{luu2016making} also implemented a symbolic execution tool \texttt{OYENTE} to find security bugs.
-A framework to analyze and verify both the runtime safety and the functional correctness of Solidity contracts in F* was presented in \cite{bhargavan2016formal}.
+A framework to analyze and verify both the runtime safety and the functional correctness of Solidity smart contracts in F* was presented in \cite{bhargavan2016formal}.
 %\end{itemize}
@@
 61772038, 61532019 and 61272160, and the Guangdong Science and Technology Department (Grant no.2018B010107004).
+Thanks to members of Cryptape, especially Jan and Zhiwei, for the helpful discussions during the development of this framework.
 

### 2020-04-26 COORDINATION2020/paper6.tex
paper update

@@
 For the tests, we perform the testing of arithematic operations against the Ethereum test suite.
-
-Generally, the central design choice of the framework is to leverage the infrastructure of 
-Why3, the deductive verification platform where a set of external theorem provers, both automated and interactive, 
-can be relied on to discharge verification conditions. At the same time, 
-OCaml programs can be directly extracted from WhyML programs through the extraction mechanism for further tests.
 }
@@
 The properties we verify are to guarantee that overflow and underflow problems would not occur in the number operations.
-Besides, the correctness of the operation results are also specified in the postconditions and further verified, for example,
+Besides, the correctness of the operation results is also specified in the postconditions and further verified, for example,
 the last postcondition in the function \texttt{div\_safe}.
@@
   (not to_int a = 0 ->
-  to_int a = ((to_int result * to_int b) + mod (to_int a) (to_int b))))
+  to_int a = (to_int result * to_int b + mod (to_int a) (to_int b))))
 \end{verbatim}
@@
 Complete proving goals derived from the functions and 
-proof sessions can be found on this website.
+proof sessions can be found at \url{https://github.com/Xiyue-Selina/coordination20}.
 }
@@
 {\xy
-\paragraph{Simple Auction contract verification}
+\paragraph{Open Auction contract verification.}
+The open auction contract is mainly comprised of three functions:
+(1)~Everyone can send their bids through the \texttt{bid} function when the bidding period is not finished.
+When the bid sent by one bidder exceed the current recorded highest bid, the auction state including the highestBidder and highestBid would be updated. Then the withdrawal amount of the previous
+highest bidder should be increased by the previous highest bid.
+(2)~When one bid is beat by another higher raised bid, the previous bid should be returned back to the
+corresponding bidder. Bidders can call \texttt{withdraw} function to get the money/Ether back.
+(3)~The auction is ended by function \texttt{auctionEnd}. If current time is over the auctionEndTime,
+then the auction \texttt{end\_state} should be set to True. As the bidding ended, the beneficiary would 
+receive the final highest Bid.
+
+In the WhyML specification, \texttt{auction\_status} records the current state of the auction including the current 
+highest bidder, the highest bid and the auction ended state. \texttt{auction\_constant} records the beneficiary and the
+auctionEndTime and \texttt{auction\_ended} records the final bidder, bid and the beneficiary claimed money/Ether amount.
+The properties to be verified are to guarantee the correctness of the functionality. For example,
+in the \texttt{auctionEnd} definition, the postcondition specifies the constraints of 
+auction ended state and beneficiary claimed amount that the returned result should satisfy.
+Complete specification of the three functions can be found at \url{https://github.com/Xiyue-Selina/coordination20}. 
+The generated verification conditions can be discharged through \emph{alt-ergo} and \emph{cvc4} automatically.
+
+\begin{verbatim}
+let auctionEnd (current_time: uint) (auc_st: auction_status) 
+(auc_const: auction_constant) (auc_end: auction_ended): 
+(auction_status, auction_ended) 
+... ensures {let (_auc_st, _auc_end) = result in 
+_auc_st.end_state = True 
+&& _auc_end.finalBidder = auc_st.highestBidder 
+&& _auc_end.finalBid = auc_st.highestBid
+&& _auc_end.bene_amount.benefici = auc_const.beneficiary 
+&& _auc_end.bene_amount.benefit_amount = _auc_end.finalBid} = ...
+\end{verbatim}
 
@@
 \section{Related Work}\label{Sec: Related}
-{\xy About comparison with KEVM framework with the support
-of ...logic, Hoare logic serves as a good framework for
-verification condition specification avoiding the complex definitions
-of the operational semantics.}
 
-Research interest of blockchain technology has exploded since the inception of Bitcoin.
-As the popularity of the second generation of blockchain, Ethereum, grows, a series of security vulnerabilities have also appeared.
-Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units among multiple parties, the security of smart contracts and EVM implementations is of paramount importance.
-To address the security challenges, researchers resorted to the techniques of formal methods and program analysis.
+Research interest of blockchain technology has exploded since the inception of Bitcoin. As the popularity of the second generation of blockchain, 
+Ethereum, grows, a series of security vulnerabilities have also appeared. 
+Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units among multiple parties, 
+the security of smart contracts and EVM implementations is of paramount importance. To address the security challenges, 
+researchers resorted to the techniques of formal methods and program analysis.
 
@@
 %    \item \textbf{Formalization Foundation of EVM} 
-An executable formal semantics of EVM has been created in the K framework by Everett et al.~\cite{hildenbrandt2017kevm}.
-Hirai~\cite{hirai2017defining} proposed an EVM implementation in Lem, a language that can be compiled for a few interactive theorem provers.
-Further, safety properties of smart contracts can be proved in proof assistants like Isabelle/HOL.
-The \texttt{hevm} project~\cite{hevm} is implemented in Haskell for unit testing and debugging smart contracts, though the EVM implementation is not completed yet.
-Besides the above formalizations of EVM, there are also implementations of EVM in other languages such as %Javascript~\cite{vmjs},
-Go~\cite{vmgo} and Ruby~\cite{cryptape}.
+{\xy\noindent\textbf{Specification and Verification.}~An executable formal semantics of EVM has been 
+created in the K framework by Everett et al.~\cite{hildenbrandt2017kevm}. 
+Compared with KEVM with the support
+of matching logic for verification, we use Hoare logic, which serves as a good framework for
+verification condition specification, to avoid the complex definitions
+of the operational semantics. 
+A framework to analyze and verify both the runtime safety and the functional correctness of 
+Solidity smart contracts in F*
+% , a functional programming language aimed at program verification,
+was presented in \cite{bhargavan2016formal}.
+Hirai~\cite{hirai2017defining} proposed an EVM implementation in Lem, a language that can be compiled for 
+a few interactive theorem provers. Then, safety properties of smart contracts can be proved in proof assistants like Isabelle/HOL.
+While in our work, we use WhyML for specification and programming, which supports both logical theories 
+and programming data structures. Moreover, both automated and interactive external theorem provers 
+can be relied on to discharge verification conditions. 
+% Generally, the central design choice of the framework is to leverage the infrastructure of 
+% Why3, the deductive verification platform where a set of external theorem provers, both automated and interactive, 
+% can be relied on to discharge verification conditions. At the same time, 
+% OCaml programs can be directly extracted from WhyML programs through the extraction mechanism for further tests.
+% Besides the above formalizations of EVM, 
+% there are also implementations of EVM in other languages such as %Javascript~\cite{vmjs}, 
+% Go~\cite{vmgo} and Ruby~\cite{cryptape}.
 %    \item \textbf{Verification of Smart Contracts}
 
-Sergey et al.~\cite{sergey2017concurrent} provided a new perspective between smart contracts and concurrent objects, based on which existing tools and insights for understanding, debugging and verifying concurrent objects can be used on smart contract behaviors.
-In \cite{luu2016making}, several new security problems were pointed out and a way to enhance the operational semantics of Ethereum was proposed to make smart contracts less vulnerable.
-Due to the difficulty of correcting the semantics of Ethereum, Luu et al.~\cite{luu2016making} also implemented a symbolic execution tool \texttt{OYENTE} to find security bugs.
-A framework to analyze and verify both the runtime safety and the functional correctness of Solidity smart contracts in F* was presented in \cite{bhargavan2016formal}.
+\noindent\textbf{Testing and Debugging.}~The \texttt{hevm} project~\cite{hevm} is implemented in Haskell for unit testing and debugging smart contracts.
+% though the EVM implementation is not completed yet. 
+Sergey et al.~\cite{sergey2017concurrent} provided a new perspective between smart contracts and concurrent objects,
+ based on which existing tools and insights for understanding, 
+ debugging and verifying concurrent objects can be used on smart contract behaviors. 
+ In \cite{luu2016making}, several new security problems were pointed out and a way to enhance the operational semantics of 
+ Ethereum was proposed to make smart contracts less vulnerable. 
+ Due to the difficulty of correcting the semantics of Ethereum, Luu et al.
+ ~\cite{luu2016making} also implemented a symbolic execution tool \texttt{OYENTE} to find security bugs.
+While in our work, executable OCaml programs can be directly extracted from WhyML programs for further tests 
+with the support of extraction mechanism.}
+%  of the deductive verification platform.
+
 %\end{itemize}

### 2020-04-26 final-3/paper.tex
paper update

--- 2020-04-26 COORDINATION2020/paper6.tex
@@
   \centering
-  \resizebox{0.8\textwidth}{!}{
-  \includegraphics{framework.pdf}
-  }
+  \includegraphics[scale=0.4]{framework.pdf}
   \caption{the Framework of Generating Verified EVM for Production Environment}
@@
   \centering
-  \resizebox{0.8\textwidth}{!}{
-  \includegraphics{runninginPE.pdf}
-  }
+  \includegraphics[scale=0.4]{runninginPE.pdf}
   \caption{Running EVM in Production Environment}
@@
 \subsection{Examples of Property Verification and Tests}
-{\xy
-In this section, we present some examples of property verification towards smart contracts and tests against Ethereum 
-test suites. 
-Specifically, we present the specification and verification of \emph{SafeMath} library and \emph{SimpleAuction} contract.
-For the tests, we perform the testing of arithematic operations against the Ethereum test suite.
-}
-{\xy
+
+We now show some examples of property verification towards smart contracts and tests against Ethereum 
+test suites. Specifically, we present the specification and verification of \emph{SafeMath} library and \emph{SimpleAuction} contract.
+For the tests, we perform the testing of arithmatic operations against the Ethereum test suite.
+
 \paragraph{Overflow/Underflow property verification.}
 We first take the example of \emph{SafeMath} from Solidity 
-library. Overflow/Underflow problems often occur when we deal with number operations. For EVM, the unsigned interger type we 
-perform arithematic operations on range from 0 to $2^{256}$, which is specified as \texttt{uint256} in the WhyML specification.
+library. Overflow/Underflow problems often occur when we deal with number operations. For EVM, the unsigned integer type we 
+perform arithmatic operations on range from 0 to $2^{256}$, which is specified as \texttt{uint256} in the WhyML specification.
 The properties we verify are to guarantee that overflow and underflow problems would not occur in the number operations.
@@
 preconditions, program expressions and postconditions.
-The first precondition expresses that the divisor should be greater than
+The first precondition specifies that the divisor should be greater than
 zero. The first postcondition states that the returned value should
 satisfy the required property with no underflow issues. The other
-two postconditions are to guarantee the operation result correctness. 
+two postconditions are to guarantee the correctness of the operation result. 
 \begin{verbatim}
@@
 Complete proving goals derived from the functions and 
-proof sessions can be found at \url{https://github.com/Xiyue-Selina/coordination20}.
-}
+proof sessions can be found at \cite{Examples}.
+%\url{https://github.com/Xiyue-Selina/coordination20}.
 
-{\xy
 \paragraph{Open Auction contract verification.}
@@
 (2)~When one bid is beat by another higher raised bid, the previous bid should be returned back to the
-corresponding bidder. Bidders can call \texttt{withdraw} function to get the money/Ether back.
-(3)~The auction is ended by function \texttt{auctionEnd}. If current time is over the auctionEndTime,
+corresponding bidder. Bidders can call the \texttt{withdraw} function to get the money/Ether back.
+(3)~The auction is ended by the \texttt{auctionEnd} function. If current time is over the auctionEndTime,
 then the auction \texttt{end\_state} should be set to True. As the bidding ended, the beneficiary would 
@@
 auction ended state and beneficiary claimed amount that the returned result should satisfy.
-Complete specification of the three functions can be found at \url{https://github.com/Xiyue-Selina/coordination20}. 
+Complete specification of the three functions can be found at \cite{Examples}.
+%\url{https://github.com/Xiyue-Selina/coordination20}. 
 The generated verification conditions can be discharged through \emph{alt-ergo} and \emph{cvc4} automatically.
@@
 
-}
-
 \section{Related Work}\label{Sec: Related}
@@
 %    \item \textbf{Formalization Foundation of EVM} 
-{\xy\noindent\textbf{Specification and Verification.}~An executable formal semantics of EVM has been 
+\noindent\textbf{Specification and Verification.}~An executable formal semantics of EVM has been 
 created in the K framework by Everett et al.~\cite{hildenbrandt2017kevm}. 
@@
 
-\noindent\textbf{Testing and Debugging.}~The \texttt{hevm} project~\cite{hevm} is implemented in Haskell for unit testing and debugging smart contracts.
+\noindent\textbf{Testing and Debugging.}~The \texttt{hevm} project~\cite{hevm} is implemented in Haskell for unit testing and debugging of smart contracts.
 % though the EVM implementation is not completed yet. 
@@
 While in our work, executable OCaml programs can be directly extracted from WhyML programs for further tests 
-with the support of extraction mechanism.}
+with the support of extraction mechanism.
 %  of the deductive verification platform.
@@
 \noindent This work has been supported by the National Natural Science Foundation of China under grant no.
-61772038, 61532019 and 61272160, and the Guangdong Science and Technology Department (Grant no.2018B010107004).
+61772038 and 61532019, and the Guangdong Science and Technology Department (Grant no.2018B010107004).
 Thanks to members of Cryptape, especially Jan and Zhiwei, for the helpful discussions during the development of this framework.

### 2020-04-27 final-3/paper.tex
paper update and Minimal EVM

@@
 
-Ever since the inception of the Bitcoin blockchain system \cite{nakamoto2008bitcoin}, cryptocurrencies have become a well-known global revolutionary phenomenon.
-Meanwhile, the decentralized blockchain system with no server or central authority, which emerges as a side product of Bitcoin and provides a continuously growing ledger of transactions being represented as a chained list of blocks distributed and maintained over a peer-to-peer network \cite{ZXDCW18}, shows great potential in carrying out secure online transactions.
+Ever since the inception of the Bitcoin blockchain system \cite{nakamoto2008bitcoin}, 
+cryptocurrencies have become a well-known global revolutionary phenomenon. 
+Meanwhile, the decentralized blockchain system with no server or central authority, which emerges as a side product of Bitcoin 
+and provides a continuously growing ledger of transactions being represented as a chained list of blocks distributed 
+and maintained over a peer-to-peer network \cite{ZXDCW18}, shows great potential in carrying out secure online transactions. 
 From then on, there have been a lot of changes and growth on the blockchain technology.
@@
 Ethereum \cite{Ethereum} extends Bitcoin's design, which can process not only transactions but also complex programs and {\em smart contracts}. 
-Smart contracts can automatically run inside a blockchain,
-making it possible to use blockchain techniques in many other application domains besides cryptocurrencies, and has attracted a lot of attention from government, finance, health, entertainment and industry.
+Smart contracts running on the blockchain 
+make it possible to use blockchain techniques in many other application domains besides cryptocurrencies, 
+and have attracted a lot of attention from government, finance, health, entertainment and industry.
 This feature makes Ethereum a popular ecosystem for building blockchain-applications, which gains much more interest to innovate the options to utilize blockchain.
@@
 %Different languages have been proposed for developing smart contracts. For example, Ethereum provides a Turing-complete programming language named {\em Solidity} to implement smart contracts.
-Smart contracts are often written in a Turing-complete programming language called \textit{Solidity} \cite{solidity} and then compiled into low-level machine instructions (\textit{opcodes}), which can be encoded into bytecode.
-Ethereum Virtual Machine (EVM) is a quasi-Turing complete machine which implements the execution model of the Ethereum Virtual Machine.
+Smart contracts are often written in a Turing-complete programming language called \textit{Solidity} \cite{solidity} 
+and then compiled into EVM bytecode, which can be mapped into a list of machine instructions (\textit{opcodes}).  
+% low-level machine instructions (\textit{opcodes}), which can be encoded into bytecode. 
+Ethereum Virtual Machine (EVM) is a quasi-Turing complete machine. 
+It provides a runtime environment for smart contracts to be executed. 
+% which implements the execution model of the Ethereum Virtual Machine. 
 Given a sequence of bytecode instructions, which are compiled from smart contracts by an EVM compiler, and the environment data, this execution model specifies how the blockchain transits from one state to another.
@@
 The adoption of formal methods can facilitate the production of trustworthy and reliable smart contracts as well.
-To deal with the security challenges against EVM, we proposed a formal framework of generating verified EVM for production environment in this paper. The contributions of this work are: 
+To deal with the security challenges against EVM, we propose a formal framework of generating verified EVM for production environment in this paper. The contributions of this work are: 
 \begin{itemize}
@@
 %Based on the framework, we perform some experiments in Section \ref{Sec: Experiment} and highlight the verification and testing results for the properties of EVM.
-Section \ref{Sec: Related} presents some related work. Finally, we summarized this paper %and point out the future research direction 
+Section \ref{Sec: Related} presents some related work. Finally, we summarize this paper %and point out the future research direction 
 in Section \ref{Sec: Conclusion}.
@@
 In this section, we present the framework of generating verified EVM for production environment in detail. 
-The framework is as shown in Fig.
-\ref{fig:evm1} and the main idea is to combine verification and testing techniques towards developing secure EVM implementations.
-It also provides the potential to verify smart contracts at the bytecode level.
-This framework is mainly comprised of two parts: EVM specification in Why3 and experimental testing based on OCaml Extraction and Rust connection.
-This approach leverages on formal methods and engineering approaches, allowing us to perform both rigorous verification and efficient testing for EVM implementations and further smart contracts.
+The framework is as shown in Fig. \ref{fig:evm1} and the main idea is to combine verification and testing techniques 
+towards developing more secure EVM implementations.
+It also provides a platform to verify the functionality properties of smart contracts.  
+This framework is mainly comprised of two parts: (1)~EVM specification and property verification in Why3; (2)~experimental testing based on OCaml extraction and Rust connection. 
+This approach leverages formal methods and engineering approaches, allowing us to perform 
+both rigorous verification and efficient testing for EVM implementations and smart contracts.
 
@@
 We develop the EVM specification, following the Ethereum project yellow paper~\cite{wood2014ethereum}. 
-More specifically, the EVM implementation is translated into WhyML, the programming and specification language of Why3.
-%Towards the verification,
-Verification conditions can be further generated through Why3 based on the EVM and property specification.
-The verification goals can be split into a set of subgoals or directly be proved through the supported Satisfiability Modulo Theories (SMT) solvers.
-In cases when the automatic SMT solvers cannot deal with, users can resort to interactive theorem provers based on the files generated by Why3.
+More specifically, the EVM implementation is translated into WhyML, 
+the programming and specification language of Why3. %Towards the verification, 
+Verification conditions can be further generated
+based on the pre- and post-condition specification. 
+Generated verification goals can be solved directly through the supported 
+Satisfiability Modulo Theories (SMT) solvers or go through a sequence of transformations first. 
+% Generated verification goals can be split into a set of subgoals or directly be proved through the supported 
+% Satisfiability Modulo Theories (SMT) solvers. 
+In cases when the automatic SMT solvers cannot deal with, users can resort to interactive theorem provers for the remaining unsolved proof goals.
 
-EVM is essentially a simple stack-based machine.
-The memory model of EVM is a word-addressed byte array, which is volatile.
-The storage model of EVM is a non-volatile word-addressed word array.
-These three components form the infrastructure of EVM.
+EVM is essentially a stack-based machine. The memory model of EVM is a word-addressed byte array and
+the storage model is a word-addressed word array. These three components form the infrastructure of EVM. 
 Based on the formalization of the infrastructure, the most important aspect in this framework is to capture the execution result of the EVM instructions. 
@@
 The formalization of base infrastructure and the instruction set are specified through \textit{Type Definition} and \textit{Instruction Definition}, respectively. 
-And the \textit{Interpreter Definition} provides the specification of the interpreter and auxiliary functions.
+The main function \textit{Interpreter} provides the specification of transition results for the instructions.
+% interpreter and auxiliary functions.
 
@@
 
-To formalize the infrastructure of EVM, we need to first provide the formalization of commonly-used types in EVM, such as the types of machine words and the addresses in the EVM.
+To formalize the infrastructure of EVM, we need to first provide the formalization of commonly-used types in EVM, 
+such as the types of machine words and the addresses in the EVM. 
 Hence, we developed a series of type modules such as \texttt{UInt256} and \texttt{UInt160} to ease the representation of corresponding types in EVM. 
@@
 Memory is defined as a function that maps \texttt{machine word} to an option type \texttt{option memory\_content}. 
-Since the memory content could be accessed through 256-bit store and 8-bit store instructions, \texttt{memory\_content} is defined as an enumeration type including \texttt{Item8} and \texttt{Item256}.
+Since the memory content could be accessed through 256-bit store and 8-bit store instructions, 
+\texttt{memory\_content} is defined as an enumeration type including \texttt{Item8} and \texttt{Item256}. 
 Similarly, storage is defined as a function that maps \texttt{machine word} to \texttt{machine word}. 
 To reflect the implicit change of the machine state, we defined more miscellaneous types. 
-For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to capture the virtual machine status, the operation error, and the view of the returned result.
-Furthermore, the record type \texttt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list, etc.
+For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to capture the virtual machine status, the operation error, 
+and the view of the returned result. 
+Furthermore, the record type \texttt{machine\_state} is defined to represent the overall machine state 
+which consists of stack, memory, storage, program counter, vmstatus, the instruction list, etc.
 
 \subsubsection{Instruction Definition}\label{sec:instruction}
-The infrastructure has been built to specify the state of the virtual machine. %Here we present the formal specification of the action set, i.e., the instruction set. 
-Inspired by the instruction formalization in Lem~\cite{hirai2017defining}, the instruction set is defined in multiple groups, such as {\em arithmetic operations} and {\em stack operations}, then these groups are integrated into a summarized type definition \texttt{instruction}.
+
+The infrastructure has been built above to specify the state of the virtual machine. 
+%Here we present the formal specification of the action set, i.e., the instruction set. 
+Inspired by the instruction formalization in Lem~\cite{hirai2017defining}, 
+the instruction set is defined in multiple groups, such as {\em arithmetic operations} and {\em stack operations}, then these groups are integrated into a summarized type definition \texttt{instruction}.
 %The definition of \texttt{instruction} is presented as follows, where
@@
 The organization of the instruction category is a bit different from the yellow paper~\cite{wood2014ethereum}. 
-The comparison operations are grouped in the arithmetic operation set \texttt{Arith}; and the comparison operations for signed arithmetic are included in the signed arithmetic operation set \texttt{Sarith}.
-The bitwise operations and operation \texttt{BYTE} are categorized into the bit-related instruction group \texttt{Bits}.
-The information related instructions including environmental and block information ones are defined in type \texttt{info\_inst}, except \texttt{CALL} and \texttt{CODE} instructions, such as \texttt{CALLDATACOPY}, \texttt{CODECOPY} and \texttt{CALLDATALOAD}.
+The comparison operations are grouped in the arithmetic operation set \texttt{Arith}; 
+and the comparison operations for signed arithmetic are included in the signed arithmetic operation set \texttt{Sarith}. 
+% The bitwise operations and operation \texttt{BYTE} are categorized into the bit-related instruction group \texttt{Bits}. 
+The information related instructions including environmental and block information are defined in type \texttt{info\_inst}, 
+except \texttt{CALL} and \texttt{CODE} instructions, such as \texttt{CALLDATACOPY}, \texttt{CODECOPY} and \texttt{CALLDATALOAD}. 
 These instructions are more closely related to memory and stack status. 
-Therefore, extra instructions but closely-related ones are added to the original memory and stack instruction groups.
-% presented in the yellow paper.
+Therefore, they are added to the memory and stack instruction groups. % presented in the yellow paper. 
 In case when some illegal command occurs, the instruction \texttt{Invalid} is included in the \texttt{instruction} definition. 
-The \texttt{STOP} operation and the system operations from the yellow paper are defined in the \texttt{System} instruction set.
+% The \texttt{STOP} operation and the system operations from the yellow paper are defined in the \texttt{System} instruction set. 
 The specification of the remaining instruction groups are basically the same as the corresponding instruction subsets in \cite{wood2014ethereum}.

### 2020-04-27 final-3/paper.tex
paper update till section 2.1

@@
 The organization of the instruction category is a bit different from the yellow paper~\cite{wood2014ethereum}. 
-The comparison operations are grouped in the arithmetic operation set \texttt{Arith}; 
-and the comparison operations for signed arithmetic are included in the signed arithmetic operation set \texttt{Sarith}. 
+% The comparison operations are grouped in the arithmetic operation set \texttt{Arith}; 
+% and the comparison operations for signed arithmetic are included in the signed arithmetic operation set \texttt{Sarith}. 
 % The bitwise operations and operation \texttt{BYTE} are categorized into the bit-related instruction group \texttt{Bits}. 
@@
 For a specific instruction, the interpreter determines the resultant machine status developing from the current status. 
-Some auxiliary functions are defined
-to make the definition of the interpreter more concise and compact.
-For example, the following function is used to obtain the next instruction to be executed.
-It is obtained from the instruction list following the program counter.
+Some auxiliary functions are defined to make the definition of the interpreter more concise and compact. 
 \begin{verbatim}
-let get_inst (mac_st: machine_state): option instruction =
-  match mac_st.mac_pc, mac_st.mac_insts with 
-  | pc, insts -> (nth pc insts) 
-  end    
+let interpreter (m: machine_state): machine_state =
+let inst = get_inst m in
+match inst with 
+  | Some (Arith ADD) -> let (st', a) = (pop_stack (m.mac_stack)) in 
+    let (st'', b) = ( pop_stack st') in ...
+    {m with mac_stack = push_stack st'' (a' + b'); ...}
 \end{verbatim}
 
-Pop and push operations are the most commonly-used manipulations for the state transition of stack.
-Auxiliary functions \texttt{push\_stack} and \texttt{pop\_stack} are defined to control the change of stack status.
-For capturing the status transition result of \texttt{Swap} instructions, recursive functions \texttt{fetch} and \texttt{drop} are defined to support more direct manipulation on lists.
-Another function \texttt{swap\_stack} is defined further for state transition of swap instructions.
-With these pre-defined auxiliary functions, the definition of the interpreter function is essentially comprised of machine status update with regard to concrete instructions.
+For example, in the above code snippet of \texttt{Arith ADD} instrcution, 
+\texttt{get\_inst} is used to obtain the next instruction to be executed. 
+It is obtained from the instruction list following the program counter. 
+% Pop and push operations are the most commonly-used manipulations for the state transition of stack. 
+Functions \texttt{push\_stack} and \texttt{pop\_stack} are defined to control the pop and push manipulations
+for the state transition of stack. 
+% For capturing the status transition result of \texttt{Swap} instructions, 
+% recursive functions \texttt{fetch} and \texttt{drop} are defined to support more direct manipulation on lists. 
+% Another function \texttt{swap\_stack} is defined further for state transition of swap instructions.
+With the support of pre-defined auxiliary functions, 
+the definition of the interpreter function is essentially comprised of machine status update with regard to the instructions.
 

### 2020-04-27 final-3/paper.tex
paper thorough revision

@@
 \subsection{EVM in Why3}
-The first phase of the framework is to define a formal specification of EVM in Why3 and provide a platform for rigorous verification.  
+The first phase of the framework is to define a formal specification of EVM in Why3 
+and provide a platform for rigorous verification.  
 We develop the EVM specification, following the Ethereum project yellow paper~\cite{wood2014ethereum}. 
@@
 based on the pre- and post-condition specification. 
-Generated verification goals can be solved directly through the supported 
-Satisfiability Modulo Theories (SMT) solvers or go through a sequence of transformations first. 
+Generated verification goals are solved directly through the supported 
+solvers or go through a sequence of transformations first. 
 % Generated verification goals can be split into a set of subgoals or directly be proved through the supported 
 % Satisfiability Modulo Theories (SMT) solvers. 
-In cases when the automatic SMT solvers cannot deal with, users can resort to interactive theorem provers for the remaining unsolved proof goals.
+In cases when the automatic SMT solvers cannot deal with, 
+users can resort to interactive theorem provers for the remaining unsolved proof goals.
 
@@
 
-To this end, the components of the base infrastructure can be easily specified. 
+To this end, the components of the base infrastructure can be specified. 
 Stack is defined as a list of elements whose type is \texttt{uint256}, aliased by \texttt{machine word}. 
 Memory is defined as a function that maps \texttt{machine word} to an option type \texttt{option memory\_content}. 
-Since the memory content could be accessed through 256-bit store and 8-bit store instructions, 
-\texttt{memory\_content} is defined as an enumeration type including \texttt{Item8} and \texttt{Item256}. 
+% Since the memory content could be accessed through 256-bit store and 8-bit store instructions, 
+% \texttt{memory\_content} is defined as an enumeration type including \texttt{Item8} and \texttt{Item256}. 
 Similarly, storage is defined as a function that maps \texttt{machine word} to \texttt{machine word}. 
 To reflect the implicit change of the machine state, we defined more miscellaneous types. 
-For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to capture the virtual machine status, the operation error, 
+For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to 
+capture the virtual machine status, the operation error, 
 and the view of the returned result. 
@@
 The specification of \texttt{interpreter} formalizes the state transition result of different instructions. 
-For a specific instruction, the interpreter determines the resultant machine status developing from the current status. 
+For a specific instruction, the interpreter determines the result machine state developing from the current state. 
 Some auxiliary functions are defined to make the definition of the interpreter more concise and compact. 
@@
   | Some (Arith ADD) -> let (st', a) = (pop_stack (m.mac_stack)) in 
-    let (st'', b) = ( pop_stack st') in ...
+    let (st'', b) = (pop_stack st') in ...
     {m with mac_stack = push_stack st'' (a' + b'); ...}
@@
 
-For example, in the above code snippet of \texttt{Arith ADD} instrcution, 
-\texttt{get\_inst} is used to obtain the next instruction to be executed. 
+In the above code snippet, \texttt{get\_inst} is used to obtain the next instruction to be executed. 
 It is obtained from the instruction list following the program counter. 
+In the case of \texttt{Arith ADD} instrcution, the numbers to perform the add operation on are popped out of the stack first and the
+result is pushed into the stack after the calculation. As a result, the stack state is updated as a component of the machine state.
 % Pop and push operations are the most commonly-used manipulations for the state transition of stack. 
-Functions \texttt{push\_stack} and \texttt{pop\_stack} are defined to control the pop and push manipulations
+In this process, functions \texttt{push\_stack} and \texttt{pop\_stack} are defined to control the push and pop manipulations
 for the state transition of stack. 
@@
 With the support of pre-defined auxiliary functions, 
-the definition of the interpreter function is essentially comprised of machine status update with regard to the instructions.
+the definition of the interpreter function is essentially comprised of machine state update with regard to the instructions.
 
@@
 %We customizedly defined a series of drivers to %extract WhyML programs into OCaml programs. 
-Fig.
-\ref{fig2} shows the second phase of the framework: deploy the verified EVM, encoded in Why3, in production environments.
+Fig. \ref{fig2} shows the second phase of the framework: deploy the extracted OCaml implementation from Why3 in production environments. 
 The deployment is essentially based on a co-compilation framework between OCaml and Rust.
@@
 In the latter case, a runtime library is attached to handle various non-functional features like memory management. 
-Through the \texttt{Callback} module, OCaml allows us to register a set of callback functions which can be used as an interface in static or dynamic linking.
+Through the \texttt{Callback} module, OCaml allows us to register a set of callback functions which can be used as an interface
+in static or dynamic linking. 
 So we first defined a series of customized drivers to extract WhyML programs into OCaml programs. 
@@
 
-Rust is a multi-paradigm system programming language which is designed to provide better memory safety while maintaining high performance \cite{LBHN16}.
+Rust is a multi-paradigm system programming language which is designed to provide better memory safety 
+while maintaining high performance \cite{LBHN16}.
 The framework provides the interaction mechanism between Rust and Why3. 
@@
 The coupling between Rust and extracted OCaml implementation enables us to perform VM tests to test the basic workings of the verified VM. 
-Information of the overarching environment is obtained through the interface of Rust implementation, and the test can be performed on the execution of the OCaml implementations to check the operations in different transactions.
+Information of the overarching environment is obtained through the interface of Rust implementation, 
+and the test can be performed on the execution of the OCaml implementations to check the operations in different transactions.
 
@@
 (1)~Everyone can send their bids through the \texttt{bid} function when the bidding period is not finished.
-When the bid sent by one bidder exceed the current recorded highest bid, the auction state including the highestBidder and highestBid would be updated. Then the withdrawal amount of the previous
+When the bid sent by one bidder exceeds the current recorded highest bid, the auction state including the highestBidder and highestBid would be updated. Then the withdrawal amount of the previous
 highest bidder should be increased by the previous highest bid.
-(2)~When one bid is beat by another higher raised bid, the previous bid should be returned back to the
+(2)~When one bid is beaten by another higher raised bid, the previous bid should be returned back to the
 corresponding bidder. Bidders can call the \texttt{withdraw} function to get the money/Ether back.
-(3)~The auction is ended by the \texttt{auctionEnd} function. If current time is over the auctionEndTime,
+(3)~The auction is ended by the \texttt{auctionEnd} function. If current time is already greater than the auctionEndTime,
 then the auction \texttt{end\_state} should be set to True. As the bidding ended, the beneficiary would 
@@
 auction ended state and beneficiary claimed amount that the returned result should satisfy.
-Complete specification of the three functions can be found at \cite{Examples}.
+Complete specification of the functions can be found at \cite{Examples}.
 %\url{https://github.com/Xiyue-Selina/coordination20}. 
@@
 
-Research interest of blockchain technology has exploded since the inception of Bitcoin. As the popularity of the second generation of blockchain, 
-Ethereum, grows, a series of security vulnerabilities have also appeared. 
-Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units among multiple parties, 
-the security of smart contracts and EVM implementations is of paramount importance. To address the security challenges, 
+Research interest of blockchain technology has exploded since the inception of Bitcoin. 
+As the popularity of the second generation of blockchain, 
+Ethereum, grows, a series of vulnerabilities have also appeared. 
+Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units 
+among multiple parties, 
+the safety of smart contracts and EVM implementations is of paramount importance. 
+To address these challenges, 
 researchers resorted to the techniques of formal methods and program analysis.
@@
 of the operational semantics. 
-A framework to analyze and verify both the runtime safety and the functional correctness of 
+A framework to analyze and verify the safety and the correctness of 
 Solidity smart contracts in F*
@@
 Sergey et al.~\cite{sergey2017concurrent} provided a new perspective between smart contracts and concurrent objects,
- based on which existing tools and insights for understanding, 
- debugging and verifying concurrent objects can be used on smart contract behaviors. 
+based on which existing tools for understanding and
+debugging concurrent objects can be used on smart contract behaviors. 
 In \cite{luu2016making}, several new security problems were pointed out and a way to enhance the operational semantics of 
@@
 While in our work, executable OCaml programs can be directly extracted from WhyML programs for further tests 
-with the support of extraction mechanism.
+with the support of customized drivers and extraction mechanism.
 %  of the deductive verification platform.
@@
 We propose a framework to enable formal specification, verification and testing towards EVM. 
-In this framework, the formalization of EVM is specified in WhyML, the programming and specification language of Why3.
-Based on the EVM formalization, automatic SMT solvers and interactive theorem provers provided in Why3 can be employed for verification.
+In this framework, the formalization of EVM is specified in WhyML, 
+% the programming and specification language of Why3. 
+based on which, automatic SMT solvers and interactive theorem provers can be employed for verification. 
 The OCaml implementation of EVM is extracted from the WhyML specification and then glued with Rust implementation based on the coupling framework.

### 2020-04-28 final-3/paper.tex
paper update

@@
 
-OCaml is a functional programming language where the programs can be compiled either to OCaml bytecode or executable binaries. 
-In the latter case, a runtime library is attached to handle various non-functional features like memory management. 
-Through the \texttt{Callback} module, OCaml allows us to register a set of callback functions which can be used as an interface
-in static or dynamic linking. 
-So we first defined a series of customized drivers to extract WhyML programs into OCaml programs. 
-After the extraction, the OCaml implementation of EVM is then encapsulated and exposed as a static linked library. 
-This library can be further called by the EVM host in Rust.
+OCaml is a functional programming language that shares a highly identical language definition and formal semantics with Why3. 
+Through the official OCaml code generator equipped with Why3, 
+we extract the verified specification of EVM into an executable OCaml module. 
+A JSON-based protocol is developed as a bridge between the OCaml implementation and the EVM host in Rust.
+
+% OCaml is a functional programming language where the programs can be compiled either to OCaml bytecode or executable binaries. 
+% In the latter case, a runtime library is attached to handle various non-functional features like memory management. 
+% Through the \texttt{Callback} module, OCaml allows us to register a set of callback functions which can be used as an interface
+% in static or dynamic linking. 
+% So we first defined a series of customized drivers to extract WhyML programs into OCaml programs. 
+% After the extraction, the OCaml implementation of EVM is then encapsulated and exposed as a static linked library. 
+% This library can be further called by the EVM host in Rust.
 
@@
 
+\paragraph{Testing of arithematic operations.}
+Cita-vm~\cite{citavm} is an Rust implementation of the Ethereum Virtual Machine developed by the CITAHub team. 
+In a forked version of Cita-vm, we patched the EVM interpreter by redirecting it to the OCaml implementation. 
+From the official EVM Consensus Tests~\cite{evmtests},
+we select the \emph{vmArithmeticTest} set and run the test cases. 
+The OCaml EVM implementation passes all the selected test cases and 
+proves its capability in the production environment.
+A guide of reproducing the test result can be found at \cite{Examples}.
+
 \section{Related Work}\label{Sec: Related}
